% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[]{article}
\usepackage{fontspec}
\setmainfont{Noto Serif}
\newfontfamily\arabicfont{Noto Sans Arabic}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{Lyrics and styles}\label{lyrics-and-styles}

\textbf{Director:} rataflechera (Carlos Thompson)\\
\textbf{Producer:} Suno\\
\textbf{Lyrics:} Some songs and sections are composed by Carlos
Thompson; others are AI-generated (using Suno, Claude, ChatGPT, or
Gemini). See individual song notes for specific attribution.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Siento}\label{siento}

\subsection{Notes}\label{notes}

\subsection{Style}\label{style}

glam metal

\subsection{Lyrics}\label{lyrics}

Siento haberte amado de una forma tan profunda\\
que hoy te odio.\\
Siento dolor y siento frío\\
Siento el vacío que me explota por dentro\\
y da rabia.\\
Siento haberte querido\\
y haber fallado en decirlo\\
y siento grandemente que te hayas ido\\
sin palabras de despedida\\
sin una maldita forma de hacerme saber\\
si algo de lo que siento has sentido\\
si en algo\\
alguna vez\\
me has querido.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{A Someone or a Someone}\label{a-someone-or-a-someone}

\subsection{Notes}\label{notes-1}

\subsection{Style}\label{style-1}

In a standard pop ballad instrumental arrangement (percussion, electric
guitar, bass, keyboards), with C major - A minor - F major - G major
chord progressions, and a deep bass, almost guttural voice. soprano
vocals in the chorus. Outtro riff.

\subsection{Lyrics}\label{lyrics-1}

I seek a beautiful illusion,\\
A ghost to hold my hand,\\
To trick my heart that as I age\\
Beside me she will stand.

A second soul for quiet talk\\
Of fantasy and theme,\\
To speak of kings and politics\\
As nothing but a dream.

(a someone or a someone; a someone or a someone)

Another face to spark the fire\\
With words both wild and free,\\
Entangled in a secret game,\\
Whatever we may be.

A different hand for warm embrace\\
Beneath the silver screen,\\
To share the quiet of the night,\\
The sweetest peace unseen.

(a someone or a someone; a someone or a someone)

A partner for a wicked plot,\\
For schemes of grand design,\\
To plan a world-domination\\
With her hand placed in mine.

And one more soul to pack a bag\\
For lands we do not know,\\
To seek out wild, uncharted shores\\
Where only shadows grow.

(a someone or a someone; a someone or a someone)

I do not look for one alone\\
To bear this heavy cast,\\
To be the anchor of my world,\\
The first line and the last.

I need a crew of separate souls,\\
Each perfect in their place---\\
A different hand for every need,\\
A changing, fleeting face.

I do not look for one alone\\
To bear this heavy cast,\\
(a someone or a someone; a someone or a someone)\\
To be the anchor of my world,\\
The first line and the last.\\
(a someone or a someone; a someone or a someone)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Chiq}\label{chiq}

\subsection{Notes}\label{notes-2}

\subsection{Style}\label{style-2}

balada cubana, orchestra and piano

\subsection{Lyrics}\label{lyrics-2}

Como un ángel que llegó a mi vida\\
\strut ~hiriendo mi corazón con un dardo\\
\strut ~ implacablemente y en nada tardo\\
\strut ~~ que cupido presta ya de salida

Luminosa musa que nos inspira\\
\strut ~un fuerte murmullo que presto canta\\
\strut ~ zumbido que resuena en hora santa~\\
Bailando ese ritmo que bien admira

~esperanza aun tengo que de esto salga\\
\strut ~ alguna experiencia muy positiva\\
\strut ~~ trasendental y que la pena valga

~~~ rápido espero poder darte todo\\
\strut ~~~~ indiscutiblemente mientras viva\\
\strut ~~~~~ zanjando diferencias de otro modo

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Dead Sea's barren dreams}\label{dead-seas-barren-dreams}

\subsection{Notes}\label{notes-3}

\subsection{Style}\label{style-3}

goth metal, guttural voice

\subsection{Lyrics}\label{lyrics-3}

In yonder lands of arid climes,\\
Where virtues shine in hospitality's rhymes,\\
In Genesis' scrolls, 'neath Abraham's gaze,\\
Lies tales of honor, and treachery's haze.\\
'Twas not the love twixt men that stirred the fray,\\
But breach of kindness led astray,\\
For Sodom and Gomorrah, in their plight,\\
Fell to ruin in hospitality's blight.\\
Lot, a figure, noble and bold,\\
Did offer kin to guests, as the story is told,\\
His daughters he proffered, in sacred vow,\\
To uphold the laws of hospitality's brow.\\
Reflect on this tale, and its moral decree,\\
Homophobia? Nay, but kindness be free.\\
A fable spun, though unreal it seems,\\
To explain the Dead Sea's barren dreams.\\
Thus, let us heed, in our earthly sod,\\
The lessons of kindness, taught by God.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Mellan is och hård betong}\label{mellan-is-och-huxe5rd-betong}

\subsection{Notes}\label{notes-4}

\subsection{Style}\label{style-4}

glam metal

\subsection{Lyrics}\label{lyrics-4}

\subsubsection{Vers 1}\label{vers-1}

Hon lärde sig på frusen is\\
att falla utan ljud,\\
att bära kroppen genom ljuset\\
med disciplin som hud.

\subsubsection{Vers 2}\label{vers-2}

Nu vandrar hon bland ritningar\\
av damm och tropisk jord,\\
där gröna linjer måste växa\\
genom betongens ord.

\subsubsection{Refräng}\label{refruxe4ng}

Mellan is och hård betong,\\
mellan regn och torr savann,\\
går Erika genom världen\\
som om balansen bar henne fram.

\subsubsection{Vers 3}\label{vers-3}

Europa låg i vinterdimma,\\
kanaler, tåg och glas,\\
men söderut fanns heta vindar\\
och floder utan namn.

\subsubsection{Refräng}\label{refruxe4ng-1}

Mellan is och hård betong,\\
mellan regn och torr savann,\\
går Erika genom världen\\
som om balansen bar henne fram.

\subsubsection{Brygga}\label{brygga}

Hon planterar skugga\\
där solen aldrig tvekar.\\
Hon minns fortfarande ljudet av skridskor mot morgonis.

\subsubsection{Vers 4}\label{vers-4}

Och någonstans i kvällens hetta\\
står träd hon själv drog upp,\\
med rötter under torra städer\\
som vägrar ge sig upp.

\subsubsection{Refräng}\label{refruxe4ng-2}

Mellan is och hård betong,\\
mellan regn och torr savann,\\
går Erika genom världen\\
som om balansen bar henne fram.

\texttt{{[}riff{]}}

\subsubsection{Refräng}\label{refruxe4ng-3}

Mellan is och hård betong,\\
mellan regn och torr savann,\\
går Erika genom världen\\
som om balansen bar henne fram.

\texttt{{[}Fade{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Love's Final Name}\label{loves-final-name}

\subsection{Notes}\label{notes-5}

\subsection{Style}\label{style-5}

glam metal

\subsection{Lyrics}\label{lyrics-5}

\subsubsection{Verse 1}\label{verse-1}

She learned to turn on frozen lines\\
with balance, edge, and grace,\\
To hold a perfect shape in motion\\
while silence filled the space.

\subsubsection{Verse 2}\label{verse-2}

In Utrecht by the winter canals,\\
where green breaks through the stone,\\
She built her careful life the way\\
some gardens slowly grow.

\subsubsection{Chorus}\label{chorus}

Love does not arrive complete,\\
nor speak its final name.\\
And Erika moves softly still\\
across the ice and rain.

\subsubsection{Verse 3}\label{verse-3}

She never asked the heart to swear\\
what time had not made true,\\
Some bonds were held like thawing lakes\\
beneath a silver moon.

\subsubsection{Chorus}\label{chorus-1}

Love does not arrive complete,\\
nor speak its final name.\\
And Erika moves softly still\\
across the ice and rain.

\subsubsection{Bridge}\label{bridge}

A distant train.\\
A hotel light.\\
A hand she does not pull away from.

\subsubsection{Verse 4}\label{verse-4}

The rink lights hum beyond the glass,\\
her blades still carve the white,\\
And somewhere far from Stockholm now\\
she lets the door stay slight.

\subsubsection{Chorus}\label{chorus-2}

Love does not arrive complete,\\
nor speak its final name.\\
And Erika moves softly still\\
across the ice and rain.

\texttt{{[}riff{]}}

\subsubsection{Chorus}\label{chorus-3}

Love does not arrive complete,\\
nor speak its final name.\\
And Erika moves softly still\\
across the ice and rain.

\texttt{{[}Fade{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Burn the Glass}\label{burn-the-glass}

\subsection{Notes}\label{notes-6}

Lyrics and production by Gemini

\subsection{Style}\label{style-6}

Hard rock with heavy metal influences. Distorted electric guitars play
palm-muted power chord riffs and syncopated rhythmic patterns.
Aggressive male vocals utilize a gritty, shouted delivery. The drums
feature a prominent snare with a sharp crack and a driving kick drum
pattern. A distorted bass guitar follows the guitar riffs closely. The
track features a high-gain guitar solo with rapid alternate picking and
wide vibrato. 145 BPM, 4/4 time signature, key of E minor.

\subsection{Lyrics}\label{lyrics-6}

\subsubsection{Intro}\label{intro}

\texttt{{[}distorted\ electric\ guitar\ riff,\ driving\ drums,\ bass\ enters{]}}

\subsubsection{Verse 1}\label{verse-1-1}

\texttt{{[}gritty\ male\ vocals{]}}\strut \\
These empty pockets and this restless brain\\
Keep screaming out my name in vain\\
These comfort zones are shackles I can't break\\
A soul-crushing compromise I have to make\\
I'd burn this static life and hit the gas\\
And watch it all explode behind the glass\\
A different kind of life beyond the static\\
A different kind of life yes automatic

\subsubsection{Chorus}\label{chorus-4}

\texttt{{[}full\ band\ intensity,\ crash\ cymbals{]}}\strut \\
\texttt{{[}unintelligible{]}}

\texttt{{[}Guitar\ Solo{]}}\strut \\
\texttt{{[}high-gain\ distorted\ guitar\ solo,\ rapid\ picking,\ wah-wah\ effect{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{A Drunk Without A Drop}\label{a-drunk-without-a-drop}

\subsection{Notes}\label{notes-7}

Lyrics and production by Gemini

\subsection{Style}\label{style-7}

Indie folk ballad featuring a baritone male vocal. The arrangement
centers on a fingerpicked acoustic guitar playing a steady eighth-note
pattern. A clean electric guitar provides melodic counterpoint with
light reverb and occasional slides. The bass guitar plays sustained root
notes on the downbeats. A subtle percussion layer consists of a soft
shaker and a dampened kick drum on beats one and three. The tempo is 74
BPM in 4/4 time, in the key of C major.

\subsection{Lyrics}\label{lyrics-7}

\subsubsection{Intro}\label{intro-1}

\texttt{{[}fingerpicked\ acoustic\ guitar,\ soft\ shaker{]}}

\subsubsection{Verse 1}\label{verse-1-2}

\texttt{{[}baritone\ male\ vocals{]}}\strut \\
I put off what I ought to do\\
To numb the growing dread
\texttt{{[}clean\ electric\ guitar\ enters\ with\ light\ reverb{]}}\\
A heavy dose of doing naught\\
To calm my anxious head\\
But failure breeds a sharper fear\\
A trap I can't flee
\texttt{{[}bass\ guitar\ enters\ with\ sustained\ root\ notes{]}}\\
I am a drunk without a drop\\
Undone by staying free
\texttt{{[}dampened\ kick\ drum\ on\ beats\ 1\ and\ 3{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{The Bitter Toll}\label{the-bitter-toll}

\subsection{Notes}\label{notes-8}

Lyrics and production by Gemini

\subsection{Style}\label{style-8}

Pop rock with elements of musical theater. Features a clean electric
guitar playing palm-muted eighth-note arpeggios, a melodic electric
bass, and a standard drum kit with a prominent snare. A baritone male
vocal delivers a theatrical, narrative performance with clear diction.
The arrangement builds with sustained electric guitar chords and driving
eighth-note kick patterns. Key of D major, 145 BPM, 4/4 time signature.

\subsection{Lyrics}\label{lyrics-8}

\subsubsection{Intro}\label{intro-2}

\texttt{{[}clean\ electric\ guitar\ arpeggio,\ palm-muted{]}}

\subsubsection{Verse 1}\label{verse-1-3}

\texttt{{[}baritone\ male\ vocals{]}}\strut \\
The hardest part of all of this, the bitter stinging pill
\texttt{{[}bass\ enters{]}}\\
Is every hint I'm handed down is how I should fulfill\\
My duties to the world outside to ease their care and strain
\texttt{{[}drums\ enter,\ driving\ eighth-note\ kick{]}}\\
While not a single word is meant to heal my hidden pain

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Diana carries her own
gravity}\label{diana-carries-her-own-gravity}

\subsection{Notes}\label{notes-9}

\subsection{Style}\label{style-9}

R\&B and traditional Arabic and Moroccan instrumentation.

\subsection{Lyrics}\label{lyrics-9}

\subsubsection{Verse 1}\label{verse-1-4}

Her father built his towers tall\\
on Casablanca sand,\\
and watched his daughter learn the world\\
as only daughters can.

She sat beside the men who talked,\\
outside the door they drew,\\
and memorized the way that power\\
moves before it moves.

\subsubsection{Verse 2}\label{verse-2-1}

She studied business first in Paris,\\
London gave her more,\\
then Cordon Bleu for only her ---\\
that's what the kitchens were.

Not for the firm, not for the name,\\
not what a father needs,\\
just terracotta at her lips\\
and salt, and what she pleased.

\subsubsection{Pre-chorus}\label{pre-chorus}

But somewhere in the moving\\
she began to see the shape ---\\
the choosing not to settle\\
is its own kind of escape.

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-5}

She carries her own gravity,\\
no orbit holds her long.\\
She knows the cost of staying still\\
and keeps on moving on.

\subsubsection{Verse 3}\label{verse-3-1}

In Ibiza she saw him working\\
every corner of the room,\\
and let him think they'd never met ---\\
she'd waited three years for the bloom.\\
He checked her Instagram by morning,\\
found out what she'd always known.\\
The asymmetry amused her.\\
She had never been his to own.

\subsubsection{Pre-chorus}\label{pre-chorus-1}

But somewhere in the laughing\\
she began to feel the weight ---\\
depth might not require stopping.\\
She hasn't solved it. Yet. Too late?

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-6}

She carries her own gravity,\\
no orbit holds her long.\\
She knows the cost of staying still\\
and keeps on moving on.

\subsubsection{Verse 4}\label{verse-4-1}

She moves through Paris, London, Tunis,\\
through empty legs and borrowed nights,\\
through airport hotels with Susana,\\
through all the odd and decent lights.

Lucía she watches like a lesson ---\\
a woman who kept her own ground.\\
Diana's thirty-three and noticing\\
the thing she's circling around.

\subsubsection{Bridge}\label{bridge-1}

She is not opposed to depth.\\
She is opposed to what depth costs ---\\
the stillness, the expected shape,\\
the version of herself she'd lose.

But the if is doing heavy lifting now,\\
and she can feel it in the room\\
the way she felt him in Casablanca,\\
years before he knew her name.

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-7}

She carries her own gravity,\\
no orbit holds her long.\\
She knows the cost of staying still\\
and keeps on moving on.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Diana porte sa propre
gravité}\label{diana-porte-sa-propre-gravituxe9}

\subsection{Notes}\label{notes-10}

\subsection{Style}\label{style-10}

fast-paced blend of chanson française and Mediterranean pop. It
incorporates traditional Moroccan instrumentation like the oud and
darbuka

\subsection{Lyrics}\label{lyrics-10}

\subsubsection{Verse 1}\label{verse-1-5}

Son père a bâti ses tours de pierre\\
sur le sable de Casablanca,\\
et regardé sa fille apprendre\\
ce que les hommes ne voient pas.

Elle écoutait aux portes closes,\\
assise à l'ombre des grands noms,\\
et retenait comment les choses\\
bougent avant qu'on les voit bouger.

\subsubsection{Verse 2}\label{verse-2-2}

Paris lui a donné les chiffres,\\
Londres le reste du calcul,\\
puis le Cordon Bleu pour elle seule ---\\
ça, c'était pour elle seule.

Pas pour la firme, pas le père,\\
pas pour ce qu'on attendait d'elle ---\\
juste le terracotta aux lèvres,\\
le sel, et ce qui lui plaît.

\subsubsection{Pre-chorus}\label{pre-chorus-2}

Mais quelque part dans le mouvement\\
elle a commencé à voir ---\\
que choisir de ne pas s'arrêter,\\
c'est aussi une façon de fuir.

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-8}

Elle porte sa propre gravité,\\
aucune orbite ne la tient.\\
Elle sait ce que coûte l'immobilité\\
et continue son chemin.

\subsubsection{Verse 3}\label{verse-3-2}

À Ibiza elle l'a vu travailler\\
chaque coin de la salle,\\
et l'a laissé croire qu'ils se rencontraient ---\\
elle attendait ça depuis trois ans.

Il a vérifié son Instagram le matin,\\
compris ce qu'elle savait depuis toujours.\\
L'asymétrie l'amusait.\\
Elle n'avait jamais été à lui.

\subsubsection{Pre-chorus}\label{pre-chorus-3}

Mais quelque part dans le rire\\
elle a commencé à sentir ---\\
que la profondeur n'exige peut-être pas\\
qu'on s'arrête pour la saisir.

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-9}

Elle porte sa propre gravité,\\
aucune orbite ne la tient.\\
Elle sait ce que coûte l'immobilité\\
et continue son chemin.

\subsubsection{Verse 4}\label{verse-4-2}

Elle traverse Paris, Londres, Tunis,\\
les vols vides et les nuits d'emprunt,\\
les hôtels d'aéroport avec Susana,\\
toutes ces lumières étranges et bonnes.

Elle regarde Lucía comme une leçon ---\\
une femme qui a gardé son propre poids.\\
Diana a trente-trois ans et commence\\
à voir ce qu'elle contourne depuis longtemps.

\subsubsection{Bridge}\label{bridge-2}

Elle n'est pas contre la profondeur.\\
Elle est contre ce qu'elle coûte ---\\
l'immobilité, la forme attendue,\\
la version d'elle-même qu'elle perdrait.

Mais le si porte trop de choses maintenant,\\
et elle le sent dans la pièce\\
comme elle le sentait à Casablanca,\\
des années avant qu'il sache son nom.

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-10}

Elle porte sa propre gravité,\\
aucune orbite ne la tient.\\
Elle sait ce que coûte l'immobilité\\
et continue son chemin.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{A Drunk Without A Drop
(Remix)}\label{a-drunk-without-a-drop-remix}

\subsection{Notes}\label{notes-11}

\subsection{Style}\label{style-11}

Indie folk ballad featuring a baritone male vocal. The arrangement
centers on a fingerpicked acoustic guitar playing a steady eighth-note
pattern. A clean electric guitar provides melodic counterpoint with
light reverb and occasional slides. The bass guitar plays sustained root
notes on the downbeats. A subtle percussion layer consists of a soft
shaker and a dampened kick drum on beats one and three. The tempo is 74
BPM in 4/4 time, in the key of C major.

\subsection{Lyrics}\label{lyrics-11}

\subsubsection{Intro}\label{intro-3}

\texttt{{[}fingerpicked\ acoustic\ guitar,\ soft\ shaker{]}}

\subsubsection{Verse 1}\label{verse-1-6}

\texttt{{[}male\ bass\ vocals{]}} I put off what I ought to do\\
To numb the growing dread,\\
A heavy dose of doing naught\\
To calm my anxious head.

\subsubsection{Verse 2}\label{verse-2-3}

But failure breeds a sharper fear,\\
A trap I cannot flee---\\
I am a drunk without a drop,\\
undone by staying free.

\subsubsection{Pre-chorus}\label{pre-chorus-4}

The anxiety of functional adult livehood.\\
The anxiety of the trap to fail.

\subsubsection{Chorus}\label{chorus-11}

An alcoholic who doesn't drink\\
(without a drop)\\
Procrastination, a numbing drug\\
(staying free)\\
I am a drunk without a drop,\\
undone by staying free.

\subsubsection{Verse 3}\label{verse-3-3}

The heavy chains of shifting gears\\
Are dragging at my chest,\\
The constant race to buy and build\\
Without a moment's rest.

\subsubsection{Pre-chorus}\label{pre-chorus-5}

The anxiety of functional adult livehood.\\
Heavy chains dragging at my chest.

\subsubsection{Chorus}\label{chorus-12}

An alcoholic who doesn't drink\\
(without a drop)\\
Procrastination, a numbing drug\\
(staying free)\\
I am a drunk without a drop,\\
undone by staying free.

\subsubsection{Verse 4}\label{verse-4-3}

And so I turn the screen ahead\\
To flee the breaking storm,\\
A chosen dark to block the light\\
And keep the panic warm.

\subsubsection{Pre-chorus}\label{pre-chorus-6}

Endless projects nobody else cares.\\
Scrolling, daydreaming 'till the end.

\subsubsection{Chorus}\label{chorus-13}

An alcoholic who doesn't drink\\
(without a drop)\\
Procrastination, a numbing drug\\
(staying free)\\
I am a drunk without a drop,\\
undone by staying free.

\texttt{{[}guitar\ riff{]}}

I am a drunk without a drop,\\
undone by staying free.

\texttt{{[}fade{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{The Bitter Toll (Remix)}\label{the-bitter-toll-remix}

\subsection{Notes}\label{notes-12}

\subsection{Style}\label{style-12}

Pop rock with elements of musical theater. Features a clean electric
guitar playing palm-muted eighth-note arpeggios, a melodic electric
bass, and a standard drum kit with a prominent snare. A baritone male
vocal delivers a theatrical, narrative performance with clear diction.
The arrangement builds with sustained electric guitar chords and driving
eighth-note kick patterns. Key of D major, 145 BPM, 4/4 time signature.

\subsection{Lyrics}\label{lyrics-12}

\subsubsection{Intro}\label{intro-4}

\texttt{{[}clean\ electric\ guitar\ arpeggio,\ palm-muted{]}}

\subsubsection{Verse 1}\label{verse-1-7}

\texttt{{[}baritone\ male\ vocals{]}}\strut \\
The hardest part of all of this, the bitter stinging pill
\texttt{{[}bass\ enters{]}}\\
Is every hint I'm handed down is how I should fulfill

\subsubsection{Verse 2}\label{verse-2-4}

My duties to the world outside to ease their care and strain
\texttt{{[}drums\ enter,\ driving\ eighth-note\ kick{]}}\\
While not a single word is meant to heal my hidden pain

\subsubsection{Pre-chorus}\label{pre-chorus-7}

High-functioning they call it. Or lower support needs\\
The friction, the failure, the pain is real

\subsubsection{Chorus}\label{chorus-14}

I wear a face that is not mine,\\
A perfectly constructed line,\\
To hide the storm that breaks within\\
Beneath a smooth, polite skin.\\
The cost is heavy, dark, and deep,\\
A tireless guard I have to keep.

\subsubsection{Verse 3}\label{verse-3-4}

They tell me where my hands should build,\\
What structures I must raise,\\
And measure out my worthiness\\
By maps of public praise.

\subsubsection{Pre-chorus}\label{pre-chorus-8}

High-functioning they call it. 'cause society forget\\
The friction, the failure, the pain is real

\subsubsection{Chorus}\label{chorus-15}

I wear a face that is not mine,\\
A perfectly constructed line,\\
To hide the storm that breaks within\\
Beneath a smooth, polite skin.\\
The cost is heavy, dark, and deep,\\
A tireless guard I have to keep.

\subsubsection{Verse 4}\label{verse-4-4}

Yet deep within, a quiet drought\\
Is begging for a spark,\\
A sudden shock of neon light\\
To break this heavy dark.

\subsubsection{Bridge}\label{bridge-3}

The need to be and to be seen\\
The need to connect without a judgement\\
The need to fulfill\\
The need to achieve something\\
That I can call mine

\subsubsection{Chorus}\label{chorus-16}

I wear a face that is not mine,\\
A perfectly constructed line,\\
To hide the storm that breaks within\\
Beneath a smooth, polite skin.\\
The cost is heavy, dark, and deep,\\
A tireless guard I have to keep.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Back Seat Proposal}\label{back-seat-proposal}

\subsection{Notes}\label{notes-13}

\subsection{Style}\label{style-13}

Electronic, house

\subsection{Lyrics}\label{lyrics-13}

\subsubsection{Verse 1}\label{verse-1-8}

\texttt{{[}female\ voice{]}}\strut \\
\texttt{{[}whispering{]}} Sylvia vanished past the gate,\\
the second wave still humming,\\
and Gabi called her ``curfew complication''\\
like that explained the whole thing.\\
Thomas tried assembling reasons\\
clean enough to say,\\
but every answer sounded false\\
the moment it took shape.

\subsubsection{Pre-Chorus}\label{pre-chorus-9}

Thank you, Gabi.\\
You're welcome.\\
The silence settled strange.\\
She knew the pauses in his head\\
before he tried explaining.

\subsubsection{Chorus}\label{chorus-17}

Thomas never lacked for language,\\
only words that fit the truth.\\
Every label felt dishonest\\
once it got too close to use.

And Gabi held his hand like someone\\
already reading through the act,\\
while Thomas searched for perfect phrasing\\
and kept arriving after facts.

\subsubsection{Verse 2}\label{verse-2-5}

Billboards, tunnels, rainfall thresholds,\\
train signals in the dark,\\
the toll booth girl with beautiful eyes,\\
the geometry of sparks.

Gabi kissed him in the backseat,\\
called him Blödsmann, called him fool,\\
while one half of him stayed present there\\
and one kept mapping routes.

\subsubsection{Pre-Chorus}\label{pre-chorus-10}

And somewhere in the fractured noise\\
beneath the city glow,\\
he realized she was one of few\\
he never had to perform for.

\subsubsection{Chorus}\label{chorus-18}

Thomas never lacked for feeling,\\
only structures built to last.\\
He could diagram affection\\
yet still miss what had just passed.

And Gabi laughed at every system\\
he constructed in his mind,\\
like she understood the man himself\\
beneath the overdesigned.

\subsubsection{Bridge}\label{bridge-4}

``Marry me,'' Thomas thought---\\
and instantly withdrew it.\\
Not because he feared the closeness,\\
but because the word polluted it.

Not possession.\\
Not performance.\\
Not some contractual life.\\
Just Gabi somewhere in his orbit\\
without girlfriend, fiancée, wife.

\subsubsection{Verse 3}\label{verse-3-5}

The hangar lights at Teterboro\\
cut silver through the rain,\\
and Thomas asked about her passport\\
trying not to sound insane.

She reached for reasons not to go:\\
the studio, the work, Mariain---\\
and Thomas noticed every answer\\
carefully avoiding no.

\subsubsection{Pre-Chorus}\label{pre-chorus-11}

``Official plus one?''\\
Gabi laughed.\\
The structure somehow held.\\
Not romance in the usual sense,\\
but something stranger built as well.

\subsubsection{Chorus}\label{chorus-19}

Thomas never lacked for meaning,\\
only confidence in names.\\
The closer something came to truth,\\
the less conventional it became.

And when Sandra asked ``¿Viene?'' softly\\
standing by the jetway blue,\\
Thomas answered with the simplest word\\
he fully knew was true.

\subsubsection{Outro}\label{outro}

A second wave.\\
A black car ride.\\
New York reduced to lights.\\
And two dumbasses building something\\
neither one could classify.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Peccato bello}\label{peccato-bello}

\subsection{Notes}\label{notes-14}

\subsection{Style}\label{style-14}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-14}

\subsubsection{Intro}\label{intro-5}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
Peccato d'aprile, peccato mio ---\\
\texttt{{[}record\ scratch{]}}\strut \\
ho scelto di crescere fuori dal recinto,\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
non per cadere ma per capire dove finisce la bambina\\
e dove inizio.

\subsubsection{Chorus}\label{chorus-20}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
Peccato d'aprile, e lo rifaccio ---\\
il mondo era piccolo, io ero grande,\\
e quella notte ho bruciato il calendario\\
per diventare quello che già ero.

\subsubsection{Outro}\label{outro-1}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
Doopi-do-doos Peccato d'aprile, peccato bello ---\\
non chiedo perdono a nessun cielo,\\
ho preso il mondo con le mie mani e l'ho piegato verso di me.\\
Peccato d'aprile --- era il mio, era aprile, ero io.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Comfort Zones}\label{comfort-zones}

\subsection{Notes}\label{notes-15}

\subsection{Style}\label{style-15}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-15}

\subsubsection{Intro}\label{intro-6}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
These empty pockets and this restless brain\\
\texttt{{[}record\ scratch{]}}\strut \\
Keep screaming out my name in vain\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
These comfort zones are shackles I can't break\\
A soul-crushing compromise I have to make

\subsubsection{Chorus}\label{chorus-21}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
I'd burn this static life and hit the gas\\
And watch it all explode behind the glass

\subsubsection{Outro}\label{outro-2}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
A different kind of life beyond the static\\
A different kind of life less automatic

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Andrea at Break}\label{andrea-at-break}

\subsection{Notes}\label{notes-16}

\subsection{Style}\label{style-16}

Jazz ballad with swung brushed drums, walking upright bass, muted
trumpet replies, and brushed piano comping; verse keeps it intimate and
conversational, pre-chorus lifts with chromatic turnarounds, chorus
opens into a warm hook with doubled lead and soft gang hummed answers.
Bridge strips to bass and voice, then final chorus blooms with sax
fills, delay throws on the name, and a smoky, close-mic mix that feels
satin-warm and lived-in., jazz, stylish, strong, warm

\subsection{Lyrics}\label{lyrics-16}

\subsubsection{Verse 1}\label{verse-1-9}

In the coffee room, she stands\\
Phone in one sure hand\\
Overcooked black coffee\\
Warm as a worn-out plan

Hazel eyes take in the room\\
Kindness in her face\\
Small mole on her right cheek\\
Grace in every place

\subsubsection{Pre-Chorus}\label{pre-chorus-12}

She's been through the fire\\
Still she walks in light\\
Two boys on her heart\\
And she holds them right

\subsubsection{Chorus}\label{chorus-22}

Andrea Lilliana\\
Soft but never small\\
Andrea Lilliana\\
You can feel it all\\
Golden ring, steel soul\\
She keeps rising tall\\
Andrea Lilliana\\
Still loves through it all

\subsubsection{Verse 2}\label{verse-2-6}

White silk blouse, teal jacket\\
Brown curls with red inside\\
Dimples when she smiles at you\\
Like the world just sighed

She reads the room so gently\\
Makes the hard days smooth\\
Clients trust her language\\
Colleagues feel that truth

\subsubsection{Pre-Chorus}\label{pre-chorus-13}

She's been through the fire\\
Still she walks in light\\
Two boys on her heart\\
And she holds them right

\subsubsection{Chorus}\label{chorus-23}

Andrea Lilliana\\
Soft but never small\\
Andrea Lilliana\\
You can feel it all\\
Golden ring, steel soul\\
She keeps rising tall\\
Andrea Lilliana\\
Still loves through it all

\subsubsection{Bridge}\label{bridge-5}

Snake on her wrist, alive\\
Ruby eyes that gleam\\
Every scar she carries\\
Tells a stronger dream

Swiping through the hours\\
Hope still in her hand\\
Looking for the one\\
Who can understand

\subsubsection{Chorus}\label{chorus-24}

Andrea Lilliana\\
Soft but never small\\
Andrea Lilliana\\
You can feel it all\\
Golden ring, steel soul\\
She keeps rising tall\\
Andrea Lilliana\\
Still loves through it all

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Boynton Bound}\label{boynton-bound}

\subsection{Notes}\label{notes-17}

\subsection{Style}\label{style-17}

Country rap with driving acoustic strums, snap-clap backbeat, and a fast
two-step feel; verse rides tight storytelling with fiddle fills,
pre-chorus tightens on muted bass and handclaps, chorus opens with
stacked harmonies and a chantable hook, rap bridge drops to half-time
with dry kick and talk-sung cadence, final chorus adds gang vocals and a
steel-guitar lift. Lead vocal is close-mic and gritty, with doubled hook
lines, reply shouts, and a few delay throws on key words. Ear candy
includes banjo turnarounds, reverse cymbal swells, and a radio-style
stop before the last lift. Mix is bright, punchy, and road-dust clear.,
rap, emotional, country

\subsection{Lyrics}\label{lyrics-17}

\subsubsection{Verse 1}\label{verse-1-10}

She works in West Palm\\
Paralegal suit, neat hair\\
Miami case on her phone\\
Boynton Beach by night\\
Every time she heads south\\
She comes back glowing\\
More radiant\\
More gone

\subsubsection{Pre-Chorus}\label{pre-chorus-14}

I saw the change\\
In the way she looked away\\
Keys on the counter\\
Late calls, long days\\
So I paid a man\\
To walk her shadow\\
He said, ``Just office hours''\\
But that ain't the whole road

\subsubsection{Chorus}\label{chorus-25}

Tell me what I got\\
Tell me what I don't\\
Tell me what I need\\
When the truth won't show\\
Miami runs deep\\
But it don't run clean\\
I can feel the distance\\
Cutting through me

\subsubsection{Verse 2}\label{verse-2-7}

The PI found a junior\\
A lawyer down in town\\
Coffee after work\\
Then walking around\\
No hands, no kisses\\
Just a look too long\\
Like a secret getting dressed\\
In an office light song

\subsubsection{Pre-Chorus}\label{pre-chorus-15}

Then she said, ``Big case''\\
Trips got more frequent\\
Every drive to Miami\\
Made her harder to read\\
The PI called back\\
Same parking deck, same stair\\
Still nothing I can hold\\
Still nothing in the air

\subsubsection{Chorus}\label{chorus-26}

Tell me what I got\\
Tell me what I don't\\
Tell me what I need\\
When the truth won't show\\
Miami runs deep\\
But it don't run clean\\
I can feel the distance\\
Cutting through me

\texttt{{[}Rap\ Bridge{]}}\strut \\
Old friend hit my line\\
From that other life\\
Where I trained men hard\\
In the dust and the night\\
He said, ``John, listen close\\
She's got a target''\\
And that lawyer too\\
Same shadow, same market

I laughed in the glass\\
Said, ``I don't care''\\
If they come up dead\\
I won't shed a tear\\
Then I caught myself\\
Thought of my own name\\
Colleagues know my story\\
And they'd point my way

\subsubsection{Verse 3}\label{verse-3-6}

We drank too long\\
Went through every angle\\
Who'd ask, who'd know\\
Which lie would tangle\\
By sunrise I was sick\\
Head full of smoke\\
But the fear stayed sharp\\
Like a line I'd wrote

\subsubsection{Bridge}\label{bridge-6}

Now I keep my mouth shut\\
Keep my hands still\\
What I thought at midnight\\
Ain't law, ain't will\\
You can lose your cool\\
And lose your whole life\\
One bad move in the dark\\
Can cut like a knife

\subsubsection{Chorus}\label{chorus-27}

Tell me what I got\\
Tell me what I don't\\
Tell me what I need\\
When the truth won't show\\
Miami runs deep\\
But it don't run clean\\
I can feel the distance\\
Cutting through me

\subsubsection{Outro}\label{outro-3}

Boynton to Miami\\
That road knows my name\\
I wake up with regret\\
And I still feel the same\\
Tell me what I got\\
Tell me what I don't

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Fiona at the Desk}\label{fiona-at-the-desk}

\subsection{Notes}\label{notes-18}

\subsection{Style}\label{style-18}

A cappella five-part pop with dubstep-inspired vocal bass, tight beatbox
kick-snare, and syncopated mouth percussion; verse stays close and dry
with lead voice over clustered harmonies, pre-chorus opens into stacked
thirds and rising oohs, chorus hits with punchy gang vocals and octave
bass hits, bridge strips to solo lead plus clipped ad-libs before a
bigger final chorus. Close-mic intimate mix with crisp transients, wide
harmony spread, breathy ear candy, and fast filter-sweep style vocal
drops., dubstep, piercing

\subsection{Lyrics}\label{lyrics-18}

\subsubsection{Intro}\label{intro-7}

Mm-mm Fiona, Fiona\\
(Levit) Mm-mm

\subsubsection{Verse 1}\label{verse-1-11}

Solo at her desk\\
Glass on, eyes locked in\\
Fiona Levit\\
Keeps the whole room still\\
Short black waves, sharp focus\\
Pink strap, red scarf sway\\
Butterfly on her shoulder\\
Like a secret on display

\subsubsection{Pre-Chorus}\label{pre-chorus-16}

Laptop glow on pale skin\\
Freckles in the light\\
Hazel eyes don't blink\\
She works that line by line\\
Nose ring, bracelets, watch tick\\
Nothing slips her mind\\
She's got the room in order\\
While the cables twist behind

\subsubsection{Chorus}\label{chorus-28}

Fiona, hold the line\\
Fiona, hold the line\\
Hands on the mess\\
Mind on the shine\\
Fiona, hold the line\\
Fiona, hold the line\\
She makes the whole thing work\\
In one clean line\\
(Fiona)

\subsubsection{Verse 2}\label{verse-2-8}

Mini-skirt, fishnets\\
Boots on the office floor\\
Adult, petite, and fearless\\
She still wants one more\\
Old files, new passwords\\
Every fix in place\\
American-British cadence\\
Soft fire in her face

\subsubsection{Pre-Chorus}\label{pre-chorus-17}

Messy desk, bright screen\\
She never loses pace\\
Concentrated silence\\
Drawn across the space\\
Almond eyes, arched brows\\
Reading every trace\\
She turns a crisis sideways\\
With a calm, exacting grace

\subsubsection{Chorus}\label{chorus-29}

Fiona, hold the line\\
Fiona, hold the line\\
Hands on the mess\\
Mind on the shine\\
Fiona, hold the line\\
Fiona, hold the line\\
She makes the whole thing work\\
In one clean line\\
(Fiona)

\subsubsection{Bridge}\label{bridge-7}

\texttt{{[}Beatbox\ break{]}}\strut \\
Mm-kh, tss, mm-kh\\
She's the kind of steady\\
That can tame the storm\\
In a crowded open office\\
She stays sharp, stays warm\\
One small motion, one clear choice\\
And the whole day turns\\
Fiona at the desk\\
Where the brightest focus burns

\subsubsection{Final Chorus}\label{final-chorus}

Fiona, hold the line\\
Fiona, hold the line\\
Hands on the mess\\
Mind on the shine\\
Fiona, hold the line\\
Fiona, hold the line\\
She makes the whole thing work\\
In one clean line\\
(Fiona) Fiona, hold the line\\
(Fiona, hold the line)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Je hais ma haine}\label{je-hais-ma-haine}

\subsection{Notes}\label{notes-19}

\subsection{Style}\label{style-19}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-19}

\subsubsection{Intro}\label{intro-8}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
Je hais ce que je sens pour toi,\\
Et je hais ce que tu me fais sentir.\\
\texttt{{[}record\ scratch{]}}\strut \\
Je hais t'aimer, et je me hais pour ça.\\
Je hais te haïr, et je me hais pour ça.\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
Je hais ce que je fais pour toi\\
Et je hais ce que je ne fais pas pour toi

\subsubsection{Chorus}\label{chorus-30}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
Je hais ce que tu me fais\ldots{}\\
Et je hais toute ma haine.

\subsubsection{Outro}\label{outro-4}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
Je hais tant ce que je hais\ldots{}\\
Que je finis en haïssant tout !

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Town and Country}\label{town-and-country}

\subsection{Notes}\label{notes-20}

\subsection{Style}\label{style-20}

Country rap with fiddle licks and muted banjo over a stomping kick;
verse rides tight acoustic strums and finger snaps, pre-chorus narrows
to bass and brushed snare, chorus opens with gang-vocal hook and steel
guitar sighs. Rap bridge cuts to half-time with talk-sung lines, then
final chorus adds handclaps, a grit-laced electric lead, and wide
harmony on the last line. Bright, punchy mix with close-mic vocals and
delay throws on names., rap, lilith, light, country

\subsection{Lyrics}\label{lyrics-20}

\subsubsection{Verse 1}\label{verse-1-12}

April twenty-two, two-thousand-four\\
Boynton Beach wakes up\\
Sarah heads south for Miami\\
John reads the paper at the table\\
Lilith drains the last of breakfast\\
Then the bus rolls by her school

\subsubsection{Chorus}\label{chorus-31}

Boynton Beach to Miami\\
(ride it out)\\
Boynton Beach to Miami\\
(hold on tight)\\
One road bends, one road breaks\\
And the whole day tips tonight

\subsubsection{Verse 2}\label{verse-2-9}

John leaves Carmen the key money\\
Then north to Palm Tree Security\\
Team briefing in West Palm Beach\\
Four men move on the bank\\
By mid-morning, phones off\\
Radio silence, hard and cold

\subsubsection{Pre-Chorus}\label{pre-chorus-18}

David's at the courthouse\\
Trying to beat the clock\\
Roberto's got the kind of news\\
That makes a whole room stop\\
Sarah picks Lilith up sick from school\\
And turns back up the coast

\subsubsection{Chorus}\label{chorus-32}

Boynton Beach to Miami\\
(ride it out)\\
Boynton Beach to Miami\\
(hold on tight)\\
One road bends, one road breaks\\
And the whole day tips tonight

\texttt{{[}Rap\ Bridge{]}}\strut \\
Seven o'clock, parking structure glow\\
Gunther by the BMW, Diablos in the low\\
Sarah calls out, asks who's Roberto\\
She's thinking timing, not the shadows in the row\\
Then hands go fast and the whole place cracks\\
One shot, then more, and there ain't no take-backs\\
Lilith in the back seat, Town and Country still\\
David on the line like ``I may not make the hill''

\subsubsection{Chorus}\label{chorus-33}

Boynton Beach to Miami\\
(ride it out)\\
Boynton Beach to Miami\\
(hold on tight)\\
One road bends, one road breaks\\
And the whole day tips tonight

\subsubsection{Outro}\label{outro-5}

Jackson lights burn white\\
Sarah doesn't come back\\
On the Turnpike, grief\\
Leaves a long black track\\
(hold on tight)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Nomad Butterfly}\label{nomad-butterfly}

\subsection{Notes}\label{notes-21}

\subsection{Style}\label{style-21}

Punk rock with industrial electronic influences. Distorted electric
guitars play palm-muted eighth notes in the verses and open power chords
in the chorus. A clean electric guitar provides melodic counterpoint
with bright, single-note lines. The bass guitar follows the root notes
of the guitar progression with a picked attack. Drums feature a driving
backbeat with eighth-note hi-hats and occasional crash cymbal accents.
Male vocals are delivered in a mid-range tenor with a slight grit. Key
of E Major. 160 BPM. 4/4 time signature.

\subsection{Lyrics}\label{lyrics-21}

\subsubsection{Intro}\label{intro-9}

\texttt{{[}distorted\ electric\ guitar\ palm-muted\ eighth\ notes,\ bass\ enters,\ driving\ drums{]}}

\subsubsection{Verse 1}\label{verse-1-13}

\texttt{{[}guitars\ muted{]}}\strut \\
She wears the red scarf like a second skin,\\
black wavy hair cut close around her face.\\
The glasses catch the light, the freckles stay,\\
a butterfly that chose a shoulder blade.

Multiple earrings, casual layers built,\\
hazel eyes that hold a room and shift.\\
She dresses like the city is a stage\\
and she's already packed and ready to lift.

\texttt{{[}guitars\ switch\ to\ open\ power\ chords,\ crash\ cymbals{]}}

\subsubsection{Verse 2}\label{verse-2-10}

\texttt{{[}guitars\ muted{]}}\strut \\
She started out in Jersey, seven years,\\
then London took her childhood and her ear.\\
UCLA for systems, Berkeley next,\\
the HP server lines were how she got here.

She built the confidence on hold-queue calls,\\
on engineers who didn't want to share.\\
The consultancy came later, clean and easy ---\\
but the grounding underneath it wasn't spare.

\subsubsection{Pre-Chorus}\label{pre-chorus-19}

\texttt{{[}Intimate{]}} She speaks in rounded vowels, London-born,\\
but every word she chooses lands as West.\\
The accent is the tell of two places held ---\\
she sounds like distance, dressed in Sunday best.

\subsubsection{Chorus}\label{chorus-34}

\texttt{{[}guitars\ switch\ to\ open\ power\ chords,\ crash\ cymbals{]}}\strut \\
Every city gets the real one.\\
Barcelona, cold November.\\
London when the cycles overlap.\\
None of them gets to remember.\\
Jersey suburbs keep her family tree,\\
Metro clubs where strobe lights blind the eye,\\
Fiona dances wild and breaks out free,\\
A shifting ghost before she says goodbye.

\subsubsection{Verse 3}\label{verse-3-7}

\texttt{{[}guitars\ muted{]}}\strut \\
New York metro when the grandparents called,\\
the subway smell, the diner, the return.\\
London for the grey and the familiar,\\
the city that first taught her not to yearn.

Barcelona holds the operational base,\\
the apartment that she actually keeps.\\
But the rotation pulls her every few months ---\\
she's most herself when nobody else sleeps.

\subsubsection{Pre-Chorus}\label{pre-chorus-20}

\texttt{{[}Intimate{]}} And every city that she cycles through\\
receives the undivided, present her.\\
She doesn't half-arrive or half-unpack ---\\
each landing is as real as the last were.

\subsubsection{Chorus}\label{chorus-35}

\texttt{{[}guitars\ switch\ to\ open\ power\ chords,\ crash\ cymbals{]}}\strut \\
Every city gets the real one.\\
Barcelona, cold November.\\
London when the cycles overlap.\\
None of them gets to remember.\\
Jersey suburbs keep her family tree,\\
Metro clubs where strobe lights blind the eye,\\
Fiona dances wild and breaks out free,\\
A shifting ghost before she says goodbye.

\subsubsection{Bridge}\label{bridge-8}

\texttt{{[}only\ bass\ beats{]}}\strut \\
\texttt{{[}Convcersational{]}} The butterfly on her shoulder\\
wasn't chosen lightly.\\
She knows what it means to land\\
and lift and land again.

Affection and desire\\
run on separate tracks for her ---\\
she doesn't confuse the warmth of a city\\
with wanting to stay forever.

She's selective. She means it\\
every single time.\\
The detachment isn't damage.\\
It's the shape of how she's built.

\subsubsection{Verse 4}\label{verse-4-5}

\texttt{{[}guitars\ muted{]}}\strut \\
A support ticket opened, stayed too long,\\
a voice she kept returning calls to hear.\\
Two years of text before they shared a room ---\\
she knew his mind before his face was clear.

His orbit runs through every city she does,\\
the same coordinates, a different gate.\\
She found that some connections hold at distance ---\\
the ones worth keeping, those can navigate.

\subsubsection{Pre-Chorus}\label{pre-chorus-21}

\texttt{{[}Intimate{]}} She didn't follow anyone's itinerary,\\
the overlap was written in the work.\\
But somewhere in the routing she found company\\
that didn't ask her pattern to convert.

\subsubsection{Chorus}\label{chorus-36}

\texttt{{[}guitars\ switch\ to\ open\ power\ chords,\ crash\ cymbals{]}}\strut \\
Every city gets the real one.\\
Barcelona, cold November.\\
London when the cycles overlap.\\
None of them gets to remember.\\
Jersey suburbs keep her family tree,\\
Metro clubs where strobe lights blind the eye,\\
Fiona dances wild and breaks out free,\\
A shifting ghost before she says goodbye.

\subsubsection{Outro}\label{outro-6}

\texttt{{[}only\ electronic\ instruments{]}}\strut \\
The red scarf in a different timezone,\\
the glasses on a new hotel desk.\\
The butterfly still on her shoulder ---\\
she never needed to be anywhere next.

\texttt{{[}Fade{]}}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Dig}\label{dig}

\subsection{Notes}\label{notes-22}

\subsection{Style}\label{style-22}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-22}

\subsubsection{Intro}\label{intro-10}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
Dig vill jag skriva om.\\
Dig har jag svrivit förr.\\
\texttt{{[}record\ scratch{]}}\strut \\
Men dig kan jag inte tänka något om.\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
Inte när du har blivit så länge bort.\\
Inte när ögonen dina har lämnat skenet i minet mitt.

\subsubsection{Chorus}\label{chorus-37}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
Inte heller när ingenting är ditt, sedan du inte finns.

\subsubsection{Outro}\label{outro-7}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
Ögonen dina, svarta ögon. Dem vill jag att bli mina.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{No sé, pero vuelve}\label{no-suxe9-pero-vuelve}

\subsection{Notes}\label{notes-23}

\subsection{Style}\label{style-23}

House with dubstep bass hits and a playful bounce, mid-tempo
four-on-the-floor verses; pre-chorus opens into filtered synth lifts and
vocal stacks; chorus drops with wobbling bass, clap snaps, and chantable
hooks. Soft peachy female vocals, lightly doubled in verses, wide
harmonies on the hook, short delay throws on key phrases, glossy risers
and a reverse swell into each drop, bright and polished mix with a
club-ready low end., female vocals, soft, dubstep, playful

\subsection{Lyrics}\label{lyrics-23}

\subsubsection{Verse 1}\label{verse-1-14}

¿Cómo me siento contigo?\\
Si ni yo lo tengo claro\\
Quiero sentarme a tu lado\\
Y decirlo sin disparos

Que yo misma me enredo\\
Cuando intento ser sincera\\
Te miro, me deshago\\
Y la boca se me queda

\subsubsection{Pre-Chorus}\label{pre-chorus-22}

Pero te pienso, te pienso\\
Aunque me cueste admitirlo\\
Si digo poco, me pierdo\\
Si digo todo, me caigo contigo

Y aunque no sepa ordenarlo\\
Sé que no quiero soltarte\\
Hay algo tuyo en mis manos\\
Que me hace temblar al tocarte

\subsubsection{Chorus}\label{chorus-38}

La necesito\\
Más de lo que puedo decir\\
La necesito\\
Y me da miedo descubrir\\
Si eres amiga\\
O si te tengo que soltar\\
La necesito\\
Y no sé cómo respirar

(La necesito)\\
(La necesito)

\subsubsection{Verse 2}\label{verse-2-11}

Habrá un día, tal vez\\
Que te pueda llamar amiga\\
O convencerme por fin\\
De bajarte de esta herida

Pero hoy no me sale\\
Ponerte en una respuesta\\
Hoy te pienso demasiado\\
Y me pierdo en la pregunta abierta

\subsubsection{Pre-Chorus}\label{pre-chorus-23}

Y si te hablo, me tiemblo\\
Y si callo, me persigues\\
Yo no sé qué estoy buscando\\
Pero tú ya lo intuyes

Déjame decirlo lento\\
Sin prometerte de más\\
Que entre lo que siento y lo que temo\\
Ya no me queda paz

\subsubsection{Chorus}\label{chorus-39}

La necesito\\
Más de lo que puedo decir\\
La necesito\\
Y me da miedo descubrir\\
Si eres amiga\\
O si te tengo que soltar\\
La necesito\\
Y no sé cómo respirar

(La necesito)\\
(La necesito)

\subsubsection{Bridge}\label{bridge-9}

No quiero mentirme\\
Ni pedirte un papel\\
Solo quiero verte\\
Y no romperme otra vez

Si eres puerto o tormenta\\
Si te quedas o te vas\\
Yo no tengo las respuestas\\
Pero te quiero mirar

\subsubsection{Final Chorus}\label{final-chorus-1}

La necesito\\
Más de lo que puedo decir\\
La necesito\\
Y me da miedo descubrir\\
Si eres amiga\\
O si te tengo que soltar\\
La necesito\\
Y no sé cómo respirar

(La necesito)\\
(La necesito)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Líneas en blanco}\label{luxedneas-en-blanco}

\subsection{Notes}\label{notes-24}

\subsection{Style}\label{style-24}

House with dubstep drops and playful female vocals, four-on-the-floor
pulse and syncopated bass wobble; verse stays airy with sparse kick,
plucked keys, and filtered handclaps, pre-chorus opens with rising synth
sweeps and stacked breaths, chorus hits wide with sub drops and chopped
vocal hooks. Soft close-mic lead, doubled on the hook, tiny ad-libs and
echo throws, with reversed swells and glittery bell flickers between
phrases. Bright, glossy, and buoyant mix with a punchy low end., soft,
playful, dubstep, female vocals, salsa

\subsection{Lyrics}\label{lyrics-24}

\subsubsection{Verse 1}\label{verse-1-15}

Y me encuentro otra vez\\
ante líneas en blanco\\
otra ocasión me llama\\
y yo me acerco despacio

Son palabras de relleno\\
mientras limpio mi mente\\
y ordeno ese huracán\\
que me baila de frente

De suscesos pasados\\
hay mariposas en guerra\\
revolotean en mi cabeza\\
y no les cierro la puerta

La belleza de unos ojos verdes\\
que me acompañaban\\
ojos ajenos, tan cercanos\\
y tan lejos al alba

\subsubsection{Pre-Chorus}\label{pre-chorus-24}

Y algo tiembla aquí dentro\\
quiere salir, quiere hablar\\
pero el miedo le pone\\
su cerrojo lunar

Una luna sonriente\\
me guiña desde Orión\\
y yo sigo juntando\\
lo que rompe mi voz

\subsubsection{Chorus}\label{chorus-40}

Líneas en blanco\\
líneas en blanco\\
yo me suelto despacio\\
(yo me suelto despacio)

Líneas en blanco\\
líneas en blanco\\
lo que callo se vuelve canto\\
(lo que callo se vuelve canto)

\subsubsection{Verse 2}\label{verse-2-12}

Una mariposa de Orión\\
cruza lento mis cielos\\
y me deja en la piel\\
un temblor tan sincero

Es el sentimiento de abandono\\
o la salsa que no sé bailar\\
tantas cosas enredadas\\
pidiendo forma al pasar

Se agolpan y se juntan\\
como vidrio y algodón\\
quieren gritarle al destino\\
quieren nombre y dirección

Pero el filtro de mis temores\\
les baja la intención\\
y sólo quedan destellos\\
sobre mi pluma en expansión

\subsubsection{Pre-Chorus}\label{pre-chorus-25}

Y algo tiembla aquí dentro\\
quiere salir, quiere hablar\\
pero el miedo le pone\\
su cerrojo lunar

Una luna sonriente\\
me guiña desde Orión\\
y yo sigo juntando\\
lo que rompe mi voz

\subsubsection{Chorus}\label{chorus-41}

Líneas en blanco\\
líneas en blanco\\
yo me suelto despacio\\
(yo me suelto despacio)

Líneas en blanco\\
líneas en blanco\\
lo que callo se vuelve canto\\
(lo que callo se vuelve canto)

\subsubsection{Bridge}\label{bridge-10}

Déjame caer\\
sin pedir perdón\\
si me tiembla la mano\\
también tiembla el corazón

Y si hoy no digo todo\\
me acerco un poco más\\
porque hasta el polvo en silencio\\
aprende a brillar

\subsubsection{Final Chorus}\label{final-chorus-2}

Líneas en blanco\\
líneas en blanco\\
yo me suelto despacio\\
(yo me suelto despacio)

Líneas en blanco\\
líneas en blanco\\
lo que callo se vuelve canto\\
(lo que callo se vuelve canto)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Rabia en la boca}\label{rabia-en-la-boca}

\subsection{Notes}\label{notes-25}

\subsection{Style}\label{style-25}

House-dubstep hybrid with bright four-on-the-floor verses and a
half-time bass drop in the chorus; playful peachy female vocals, clipped
rhythmic phrasing, stacked doubles on the hook, whispered ad-libs in the
pre-chorus, riser sweeps into each drop, reverse cymbal tails and glossy
sidechain pump, polished and punchy with a wide club-ready mix, soft,
playful, female vocals, dubstep

\subsection{Lyrics}\label{lyrics-25}

\subsubsection{Verse 1}\label{verse-1-16}

No es sabor amargo en la boca\\
ni dolor que me parta el pecho\\
es un nudo de rabia\\
desconsuelo\\
y un ``qué pasó'' por dentro

Miro atrás\\
y veo lo que pudo ser\\
lo que el tiempo fue borrando\\
sin pedir permiso\\
sin volver

Y me quedo ahí\\
con la mano temblando\\
viendo nombres en el polvo\\
de todo lo que nunca fue

\subsubsection{Pre-Chorus}\label{pre-chorus-26}

Y le echo la culpa al otro\\
para no mirarme de frente\\
y me culpo a mí\\
por la torpeza\\
por elegir mal otra vez

Se me sube la rabia\\
se me rompe la razón\\
y cuando por fin depende de mí\\
me traiciona el corazón

\subsubsection{Chorus}\label{chorus-42}

Da rabia\\
da rabia\\
me muerde la voz

Da rabia\\
da rabia\\
lo que no pasó

Y por orgullo tonto\\
cierro la puerta hoy\\
(da rabia)\\
pero por dentro sé\\
que dolió peor

\subsubsection{Verse 2}\label{verse-2-13}

Me acuerdo de esas horas\\
de las cosas que dejé\\
de las palabras viejas\\
que juraban volver

Todo aquello que mató el tiempo\\
sin tocarlo con la mano\\
todo aquello que guardé\\
como un vidrio en el costado

Y ahora frente a mí\\
cuando toca decidir\\
sale ese orgullo idiota\\
que me hace mentir

\subsubsection{Pre-Chorus}\label{pre-chorus-27}

Y le echo la culpa al otro\\
para no mirarme de frente\\
y me culpo a mí\\
por la torpeza\\
por elegir mal otra vez

Se me sube la rabia\\
se me rompe la razón\\
y cuando por fin depende de mí\\
me traiciona el corazón

\subsubsection{Chorus}\label{chorus-43}

Da rabia\\
da rabia\\
me muerde la voz

Da rabia\\
da rabia\\
lo que no pasó

Y por orgullo tonto\\
cierro la puerta hoy\\
(da rabia)\\
pero por dentro sé\\
que dolió peor

\subsubsection{Bridge}\label{bridge-11}

Ya no quiero esconderme\\
detrás de mi versión\\
ni ponerle al otro el peso\\
de mi propia decisión

Si el pasado se me rompe\\
que se rompa de una vez\\
yo también fui quien soltó todo\\
yo también dije ``después''

\subsubsection{Chorus}\label{chorus-44}

Da rabia\\
da rabia\\
me muerde la voz

Da rabia\\
da rabia\\
lo que no pasó

Y por orgullo tonto\\
abro la puerta hoy\\
(da rabia)\\
aunque me tiemble el pulso\\
ya me elegí yo

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Esfera entintada}\label{esfera-entintada}

\subsection{Notes}\label{notes-26}

\subsection{Style}\label{style-26}

House with dubstep drops, playful swung groove and half-time bass hits;
verse stays intimate and minimal with clipped synth plucks, pre-chorus
opens into rising chords and filtered tension, chorus lands with a wide
sub drop and bright vocal doubles, bridge strips to pads and heartbeat
kick before the final lift. Soft female vocals with Latin-American
pronunciation, airy stacks on hooks, delay throws on key words, reversed
swells and glittery risers between lines, glossy and dark-bright mix.,
dubstep, female vocals, soft, playful, latin

\subsection{Lyrics}\label{lyrics-26}

\subsubsection{Verse 1}\label{verse-1-17}

Palabras en hemorragia\\
salen de una esfera entintada\\
me flotan, me hechizan\\
me suben por dentro, calladas

Explotan en un remolino\\
quieren tapar mi alma\\
y no salen de verdad\\
sólo la esconden, la enredan

\subsubsection{Pre-Chorus}\label{pre-chorus-28}

Aún no entiendo qué pasó\\
qué me pasó, por qué dolió\\
mi mundo se está deshaciendo\\
en un universo negro

Pero hay destellos\\
hay una niña triste\\
que en mis recuerdos vive\\
y todavía insiste

\subsubsection{Chorus}\label{chorus-45}

Magia negra, magia negra\\
me atrapó, me atrapó\\
Magia negra, magia negra\\
y mi voz se rompió

Magia negra, magia negra\\
no me suelta, no\\
Magia negra, magia negra\\
salió de mi corazón

\subsubsection{Verse 2}\label{verse-2-14}

Desdibujó la sonrisa\\
de una amiga en un segundo\\
y al reír, al sonreír\\
me dejó sin suelo alguno

Una mano cálida aprieta la mía\\
y me oprime sin razón\\
cuando su vida ya no cabe\\
en el borde de su dolor

\subsubsection{Pre-Chorus}\label{pre-chorus-29}

Y yo no sé cargar\\
con lo que no pude ver\\
sus problemas son tan grandes\\
que me olvido de entender

Pero hay destellos\\
hay una niña triste\\
que en mis recuerdos vive\\
y todavía insiste

\subsubsection{Chorus}\label{chorus-46}

Magia negra, magia negra\\
me atrapó, me atrapó\\
Magia negra, magia negra\\
y mi voz se rompió

Magia negra, magia negra\\
no me suelta, no\\
Magia negra, magia negra\\
salió de mi corazón

\subsubsection{Bridge}\label{bridge-12}

No venía de ella\\
no venía de su luz\\
era mi propia sombra\\
mordiéndome la cruz

Lo sano se me pudre\\
lo bueno se me va\\
y en medio del silencio\\
me vuelvo a despertar

\subsubsection{Final Chorus}\label{final-chorus-3}

Magia negra, magia negra\\
me atrapó, me atrapó\\
Magia negra, magia negra\\
y mi voz se rompió

Magia negra, magia negra\\
no me suelta, no\\
Magia negra, magia negra\\
salió de mi corazón

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Si pienso en ti}\label{si-pienso-en-ti}

\subsection{Notes}\label{notes-27}

\subsection{Style}\label{style-27}

House-pop with dubstep drops, swung four-on-the-floor verses, half-time
chorus lift, and Latin American female vocals; verse stays airy with
clipped percussion and a rubbery bass pulse, pre-chorus strips to
handclaps and filtered pads, chorus opens into stacked harmonies and a
heavy wobble bass hit. Use playful lead doubles, glossy ad-lib tails,
reverse swells before drops, and a bright, punchy mix with intimate
close-mic detail., female vocals, latin, soft, dubstep, playful

\subsection{Lyrics}\label{lyrics-27}

\subsubsection{Verse 1}\label{verse-1-18}

Si pienso en una persona,\\
pienso en tu rostro.

Si pienso en una voz,\\
busco la tuya en mi memoria.

Si pienso en una mirada,\\
la imagino de tus ojos.

Si pienso en lo que nunca fue,\\
aparece tu sombra.

\subsubsection{Pre-Chorus}\label{pre-chorus-30}

Tu imagen viene,\\
sin pedir permiso.

Tus ojos, tu cabello,\\
tu boca, tu piel.

Y yo me quedo ahí,\\
sin saber qué hacer.

\subsubsection{Chorus}\label{chorus-47}

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
Lo que más deseo, eres tú\\
Lo que más deseo, eres tú

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
No sé borrarte de mí\\
No sé borrarte de mí

\subsubsection{Verse 2}\label{verse-2-15}

Si pienso en mi dolor,\\
recuerdo tus palabras.

Aquellos saludos\\
que tú no respondiste.

Si pienso en mi vida,\\
vuelvo a encontrarte.

En unas esperanzas\\
que aún no he perdido.

En unos ojos abiertos\\
mirando a todas partes,\\
exceptuándome a mí.

\subsubsection{Pre-Chorus}\label{pre-chorus-31}

Y una voz dulce\\
con palabras ásperas.

Un nombre que temo\\
pronunciar despacio.

Un rostro que no puedo\\
soltar de mi pecho.

\subsubsection{Chorus}\label{chorus-48}

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
Lo que más deseo, eres tú\\
Lo que más deseo, eres tú

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
No sé borrarte de mí\\
No sé borrarte de mí

\subsubsection{Bridge}\label{bridge-13}

Si pienso en cualquier cosa,\\
tu figura cae primero.

Visible o escondida,\\
siempre llegas tú.

Y aunque quiera negarlo,\\
me sigues encontrando.

Tu nombre en mi garganta,\\
tu recuerdo en mi piel.

\subsubsection{Final Chorus}\label{final-chorus-4}

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
Lo que más deseo, eres tú\\
Lo que más deseo, eres tú

Si pienso en ti, ahí estás tú\\
Si pienso en ti, ahí estás tú\\
En todo lo que soy\\
siempre estás tú

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{No sé, vos sabés}\label{no-suxe9-vos-sabuxe9s}

\subsection{Notes}\label{notes-28}

\subsection{Style}\label{style-28}

Latin house-dubstep with a rolling dembow pulse and half-time bass
drops; verse rides sparse kicks, palm-muted synth stabs, and a bouncy
low-end groove; pre-chorus lifts with filtered claps and rising vocal
stacks; chorus hits wider with chopped lead synths and gang doubles.
Soft close-mic female vocals, airy doubles, playful ad-libs, delay
throws, and bright punchy mix with shimmering risers and reversed
swells., female vocals, blues, rap, german hip hop, playful, soft,
latin, dubstep, rock

\subsection{Lyrics}\label{lyrics-28}

\subsubsection{Verse 1}\label{verse-1-19}

Hay veces en la existencia\\
de cualquier ser, o la mía,\\
cuando pasa un mal momento\\
y otro ya se espera.\\
La vida no se derrumba\\
si uno se agarra\\
con las uñas\\
a cualquier aliciente.

A veces, por miedo,\\
por no soltar la pelea,\\
uno deja seguir\\
lo que igual duele.\\
Y en medio de todo,\\
sin buscarlo,\\
una mirada,\\
una sonrisa,\\
un saludo.

\subsubsection{Pre-Chorus}\label{pre-chorus-32}

Y listo,\\
la vida debe continuar.\\
Los problemas,\\
después. Y esto otro va pa' vos,\\
si vos.

\subsubsection{Chorus}\label{chorus-49}

No sé, no sé\\
si te amo.\\
No sé, no sé\\
si puedo olvidarte.\\
No sé, no sé\\
si pueda perdonarte.\\
Vos sabés, vos sabés\\
que yo te miro y tiemblo.

\subsubsection{Verse 2}\label{verse-2-16}

No sé de dónde viniste\\
ni por qué lo hiciste,\\
y lo que menos comprendo\\
es por qué me importas.\\
No sé si pueda llegar\\
el día de los dos,\\
dos extraños\\
como viejos amigos\\
en la calle.

No sé\\
si pueda dejar de hacerlo,\\
si lo que siento\\
se me va a partir.\\
No sé\\
lo que estás pensando,\\
ni sé\\
cómo me vi\\
tan estúpido\\
haciendo lo que hice.

\subsubsection{Pre-Chorus}\label{pre-chorus-33}

Solo espero,\\
poder verte un día\\
y sin decir\\
ni una palabra,\\
vos entiendas\\
que todo sigue,\\
que todo sigue,\\
aunque me queme.

\subsubsection{Chorus}\label{chorus-50}

No sé, no sé\\
si te amo.\\
No sé, no sé\\
si puedo olvidarte.\\
No sé, no sé\\
si pueda perdonarte.\\
Vos sabés, vos sabés\\
que yo te miro y tiemblo.

\subsubsection{Bridge}\label{bridge-14}

Y si te veo\\
hoy de frente,\\
que no falten\\
las ganas de hablar.\\
Un gesto corto,\\
una salida,\\
y la herida\\
se pone a bailar.

No sé,\\
no sé,\\
no sé,\\
pero vuelvo.

\subsubsection{Chorus}\label{chorus-51}

No sé, no sé\\
si te amo.\\
No sé, no sé\\
si puedo olvidarte.\\
No sé, no sé\\
si pueda perdonarte.\\
Vos sabés, vos sabés\\
que yo te miro y tiemblo.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Travel Notes}\label{travel-notes}

\subsection{Notes}\label{notes-29}

\subsection{Style}\label{style-29}

House with dubstep drops, playful high-pitched female vocals,
Latin-American pronunciation, four-on-the-floor pulse, rubbery bass
hits, verse kept sparse and bouncy, pre-chorus filters up with risers
and snapped claps, chorus opens into glittering synth stabs and a
wobbling sub drop, whispered ad-libs and stacked doubles on the hook,
bright punchy mix with glossy top end, playful, electronic, dubstep,
latin, poetry, soft, female vocals

\subsection{Lyrics}\label{lyrics-29}

\subsubsection{Verse 1}\label{verse-1-20}

Chlewey closed the school gate\\
No undergrad, not yet\\
He wanted one last trip\\
One last math quest

WordPerfect screen at night\\
XT clone in the room\\
Pages full of stories\\
Then gone, too soon

\subsubsection{Pre-Chorus}\label{pre-chorus-34}

Free time on his hands\\
No class, no train\\
Just a new notebook\\
And a half-lit brain

First page, first breath\\
Ink on the line\\
What was lost in the past\\
Started shining again

\subsubsection{Chorus}\label{chorus-52}

Travel notes, travel notes\\
Turn the page, let it glow\\
Travel notes, travel notes\\
Where the old ghosts go (go, go)

China on his tongue\\
Stockholm in his bones\\
Travel notes, travel notes\\
He wrote it all alone (alone)

\subsubsection{Verse 2}\label{verse-2-17}

July took him east\\
For the China sky\\
Math Olympiads trip\\
With a writer's eye

Hèla smiled at him\\
Tunis in her name\\
For one bright moment\\
He forgot the same

Adriana's shadow\\
Slipped out of sight\\
Then the memory came back\\
By the end of the night

\subsubsection{Pre-Chorus}\label{pre-chorus-35}

Then north came the cold\\
Blue water, white streets\\
Two and a half years\\
With a new heartbeat

Scripts turned to letters\\
Pages learned to stay\\
From handwritten lines\\
To an electronic way

\subsubsection{Chorus}\label{chorus-53}

Travel notes, travel notes\\
Turn the page, let it glow\\
Travel notes, travel notes\\
Where the old ghosts go (go, go)

China on his tongue\\
Stockholm in his bones\\
Travel notes, travel notes\\
He wrote it all alone (alone)

\subsubsection{Bridge}\label{bridge-15}

Dates got worn away\\
Revision by revision\\
Some years blurred together\\
In the half-light vision

Still the words kept moving\\
Still the hand kept true\\
Lost in the timeline\\
But alive in the blue

\subsubsection{Chorus}\label{chorus-54}

Travel notes, travel notes\\
Turn the page, let it glow\\
Travel notes, travel notes\\
Where the old ghosts go (go, go)

China on his tongue\\
Stockholm in his bones\\
Travel notes, travel notes\\
He wrote it all alone (alone)

\subsubsection{Outro}\label{outro-8}

First year, last page\\
Then the rest unfolds\\
In a notebook's shadow\\
The memory holds (holds)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Güiro quemado}\label{guxfciro-quemado}

\subsection{Notes}\label{notes-30}

\subsection{Style}\label{style-30}

salsa, afro-cuban jazz, 180 BPM, male lead vocal, smooth clear vocals,
piano tumbao, trombone stabs, brass shout chorus, güiro syncopation,
tambora accents, handclap montuno, call and response chorus, minor key
montuno, dynamic breakdowns, live room reverb, tape saturation, mono low
end, bittersweet longing, urgent release

\subsection{Lyrics}\label{lyrics-30}

\subsubsection{Intro}\label{intro-11}

\texttt{{[}piano\ enters\ with\ a\ mysterious\ tumbao,\ the\ Caribbean\ güiro\ and\ the\ brass\ instruments\ with\ a\ sharp\ hit{]}}

\texttt{{[}spoken,\ piano\ only{]}}\strut \\
Y es de noche\\
una noche larga e interminable\\
donde la vigilia es un sueño\\
en donde los recuerdos se agolpan\\
atropellando a su paso\\
la poca autoestima que aún se tiene.

\subsubsection{Verse 1}\label{verse-1-21}

Y es de noche todavía, larga noche interminable,\\
con una vigilia horrible que sobre mi ser porfía.\\
La memoria en agonía va atropellando el sentido,\\
con recuerdo malherido, la poca fe que aún retengo,\\
y mientras despierto vengo voy quedándome perdido.

\subsubsection{Chorus}\label{chorus-55}

Y es noche sobre mi vida, y el recuerdo vuelve a entrar,\\
con la memoria vencida que no me deja escapar.

\texttt{{[}Instrumental\ Break,\ güiro\ and\ brass{]}}

\subsubsection{Verse 2}\label{verse-2-18}

Hay pensamientos extraños que no deben razonarse,\\
ni detenerse a mirarse como si evitaran daños.\\
Pasan dejando sus años sobre la vida y la mente,\\
capturando lentamente una razón sin razón,\\
y admiro sólo la ilusión de no pensar de repente.

\subsubsection{Chorus}\label{chorus-56}

Callo lo que necesito, mientras el momento huye,\\
y en silencio me marchito viendo el instante que fluye.

\texttt{{[}Instrumental\ Break,\ tambora\ and\ cymbals{]}}\strut \\
\texttt{{[}shouted{]}} ¡Salsa! ¡Que suene el piano! ¡Que rujan los
trombones que el sujeto calla!\\
\texttt{{[}piano\ and\ brass\ interlude{]}}

\subsubsection{Verse 3}\label{verse-3-8}

Es una espera infinita, eterna y desesperada,\\
espera desamparada que nunca se debilita.\\
Y aunque la noche se agita la sigo buscando aún,\\
sin rastro, señal ni alud, extraño palabras viejas,\\
una imagen que ya alejas desde tu invisible luz.

\subsubsection{Chorus}\label{chorus-57}

Y es noche sobre mi vida, y el recuerdo vuelve a entrar,\\
con la memoria vencida que no me deja escapar.

\subsubsection{Montuno}\label{montuno}

\texttt{{[}Call\ and\ Response,\ energetic,\ call\ and\ response\ style{]}}\strut \\
\texttt{{[}Choir:{]}} ¿Qué es lo que te preocupa?\\
\texttt{{[}Solo:{]}} Que es noche sobre mi vida.\\
\texttt{{[}Choir:{]}} ¿Qué te preocupa de eso?\\
\texttt{{[}Solo:{]}} Que el recuerdo vuelve a entrar.

\texttt{{[}Choir:{]}} ¿Qué pasa cuando te callas?\\
\texttt{{[}Solo:{]}} En silencio me marchito.\\
\texttt{{[}Choir:{]}} ¿Qué es lo que tanto callas?\\
\texttt{{[}Solo:{]}} Callo lo que necesito.

\texttt{{[}Choir:{]}} ¿Cuándo es que te marchitas?\\
\texttt{{[}Solo:{]}} Mientras el momento huye.\\
\texttt{{[}Choir:{]}} ¿Cuándo es que lo necesitas?\\
\texttt{{[}Solo:{]}} Viendo el instante que fluye.

\subsubsection{Verse 4}\label{verse-4-6}

Es mi vida la que espera, la que depende al hablar,\\
y vuelvo siempre a callar cuando el momento se fuera.\\
Mi alma entera quisiera decirte cuánto te extraño,\\
pero el silencio hace daño y las palabras no llegan.\\
Y mis pensamientos juegan a escabullirse otro año.

\subsubsection{Chorus}\label{chorus-58}

Y es noche sobre mi vida, y el recuerdo vuelve a entrar,\\
con la memoria vencida que no me deja escapar.

Callo lo que necesito, mientras el momento huye,\\
y en silencio me marchito viendo el instante que fluye.

\subsubsection{Outro}\label{outro-9}

\texttt{{[}melodic,\ free\ verse,\ fading{]}}\strut \\
Un espacio. Una oportunidad.\\
Es de nuevo la ocasión esperada.\\
\ldots{} y espero.

y calladamente vi escabullirse\\
esta última vez.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Memory Wakes}\label{memory-wakes}

\subsection{Notes}\label{notes-31}

\subsection{Style}\label{style-31}

salsa, afro-cuban jazz, 210 BPM, fast-paced, presto, male lead vocal,
smooth clear vocals, piano tumbao, trombone stabs, brass shout chorus,
güiro syncopation, tambora accents, handclap montuno, call and response
chorus, minor key montuno, dynamic breakdowns, live room reverb, tape
saturation, mono low end, bittersweet longing, urgent release

\subsection{Lyrics}\label{lyrics-31}

\subsubsection{Intro}\label{intro-12}

\texttt{{[}piano\ enters\ with\ a\ mysterious\ tumbao,\ the\ Caribbean\ güiro\ and\ the\ brass\ instruments\ with\ a\ sharp\ hit{]}}

\texttt{{[}spoken{]}\textasciigrave{}\textasciigrave{}{[}piano\ only{]}}\strut \\
And it is night\\
a long and endless night\\
where wakefulness is a dream\\
where memories crowd in crushing in their wake what little self-esteem
one still has.

\subsubsection{Verse 1}\label{verse-1-22}

\texttt{{[}lead\ voice,\ presto,\ melodic\ and\ connected{]}}\strut \\
The night extends without an end, a sleepless dream I cannot leave,\\
Where all remembered shadows bend through what remains of self-belief.\\
The hours gather, dark and slow, like voices pressing through a wall,\\
And every thought I used to know returns the moment nightfall calls.\\
The mind becomes a narrow room where memory learns at last to bloom.

\subsubsection{Chorus}\label{chorus-59}

The night returns with silent weight,\\
And memory crowds the dark again,\\
While sleepless hours accumulate\\
Like slowly falling winter rain.

\texttt{{[}Instrumental\ Break,\ güiro\ and\ brass{]}}

\subsubsection{Verse 2}\label{verse-2-19}

\texttt{{[}lead\ voice,\ presto,\ melodic\ and\ connected{]}}\strut \\
There are some thoughts that should not stay too long beneath the inward
gaze,\\
For reason slowly wears away inside its self-consuming maze.\\
Some things should simply drift along untouched by analysis or fear,\\
Because the need to name them wrong makes every hidden impulse clear.\\
And sometimes beauty asks of me no word, no thought --- just simply be.

\subsubsection{Chorus}\label{chorus-60}

I wait beside unspeaking words,\\
Afraid to lose the moment near,\\
And watch it fade without a sound\\
While silence overtakes my fear.

\texttt{{[}Instrumental\ Break,\ tambora\ and\ cymbals{]}}\strut \\
\texttt{{[}shouted{]}} ¡Salsa! ¡Que suene el piano! ¡Que rujan los
trombones que el sujeto calla!\\
\texttt{{[}piano\ and\ brass\ interlude{]}}

\subsubsection{Verse 3}\label{verse-3-9}

\texttt{{[}lead\ voice,\ presto,\ melodic\ and\ connected{]}}\strut \\
The waiting stretches through the years, a hollow motion without end,\\
I wait for life to reappear, for something lost to rise again.\\
I wait for her where she is not, in rooms grown distant from her name,\\
And still I guard each fragile thought as though the past might stay the
same.\\
I hear no voice, I see no face, yet still I leave for her a place.

\subsubsection{Chorus}\label{chorus-61}

The night returns with silent weight,\\
And memory crowds the dark again,\\
While sleepless hours accumulate\\
Like slowly falling winter rain.

\subsubsection{Montuno}\label{montuno-1}

\texttt{{[}Call\ and\ Response,\ energetic,\ call\ and\ response\ style{]}}\strut \\
\texttt{{[}Choir:\ multiple\ voices{]}} (What is it that haunts your
mind?)\\
\texttt{{[}Solo:\ lead\ voice{]}} Night has settled over me.\\
\texttt{{[}Choir:{]}} (What returns there in the dark?)\\
\texttt{{[}Solo:{]}} Every buried memory.

\texttt{{[}Choir:{]}} (What becomes of you when silent?)\\
\texttt{{[}Solo:{]}} Quietly, I start to fade.\\
\texttt{{[}Choir:{]}} (What is it you never tell?)\\
\texttt{{[}Solo:{]}} All the things I'm scared to say.

\texttt{{[}Choir:{]}} (When is it you fade away?)\\
\texttt{{[}Solo:{]}} As the moment disappears.\\
\texttt{{[}Choir:{]}} (When do you most need to speak?)\\
\texttt{{[}Solo:{]}} When the instant leaves me here.

\subsubsection{Verse 4}\label{verse-4-7}

\texttt{{[}lead\ voice,\ presto,\ melodic\ and\ connected{]}}\strut \\
My life depends on what I say, yet silence always comes too soon,\\
I search for words that drift away like fading echoes in a room.\\
And when at last the moment nears to speak the need I cannot hide,\\
I lose my courage to my fears and let the living instant slide.\\
The soul ascends toward trembling lips, then quietly the moment slips.

\subsubsection{Chorus}\label{chorus-62}

The night returns with silent weight,\\
And memory crowds the dark again,\\
While sleepless hours accumulate\\
Like slowly falling winter rain.

I wait beside unspeaking words,\\
Afraid to lose the moment near,\\
And watch it fade without a sound\\
While silence overtakes my fear.

\subsubsection{Outro}\label{outro-10}

\texttt{{[}melodic,\ free\ verse,\ fading{]}}\strut \\
Un espacio. Una oportunidad.\\
Es de nuevo la ocasión esperada.\\
\ldots{} y espero.

y calladamente vi escabullirse\\
esta última vez.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Kein Feuer}\label{kein-feuer}

\subsection{Notes}\label{notes-32}

\subsection{Style}\label{style-32}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-32}

\subsubsection{Intro}\label{intro-13}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
Liebe ist kein Feuer, das verglimmt,\\
sie brennt als viele Flammen nur als eine.\\
\texttt{{[}record\ scratch{]}}\strut \\
Und Gabriele geht den Weg entlang\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
im Dunkel und im Scheine.

\subsubsection{Chorus}\label{chorus-63}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
Sie liebte ihre Mutter aus der Ferne.\\
Sie liebte, indem sie einst gegangen.\\
Sie liebte, indem sie wiederkam.

\subsubsection{Outro}\label{outro-11}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
Liebe ist kein Feuer, das verglimmt,\\
sie brennt als viele Flammen nur als eine.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Ricochets Hangover}\label{ricochets-hangover}

\subsection{Notes}\label{notes-33}

\subsection{Style}\label{style-33}

early 2000s tv theme, action rock, nu-metal riffs, alternating duet,
male baritone, female soprano, distorted electric guitar, octave bass
lines, punchy tom fills, programmed breakbeat, chorus doubled hooks,
gated snare, dry close vocals, delay throws, half-time chorus, dynamic
breakdowns, midnight noir, urban espionage, 132 BPM

\subsection{Lyrics}\label{lyrics-33}

\subsubsection{Verse 1 - Male}\label{verse-1---male}

John wakes beneath Bogotá\\
With vomit on the floor,\\
Still chasing Lilith through the haze\\
Behind señora's door.

\subsubsection{Verse 1 - Female}\label{verse-1---female}

Müller awaits his stunning guest,\\
Manhattan's heat burns high;\\
They drop the boring contract talk\\
To buy a pizza pie.

\subsubsection{Pre-Chorus}\label{pre-chorus-36}

\texttt{{[}Male{]}} One drinks to keep the ghosts asleep,\\
\texttt{{[}Female{]}} One smiles to hide an obscure past.

\subsubsection{Chorus}\label{chorus-64}

\texttt{{[}Male{]}} Ricochets. \texttt{{[}Female{]}} Ricochets.\\
\texttt{{[}Duet{]}} A bullet strikes a distant wall\\
And still returns somehow.

\texttt{{[}Male{]}} Through Bogotá and New York lights,\\
\texttt{{[}Female{]}} Through bourbon breath and tailored lies,\\
\texttt{{[}Duet{]}} Two strangers orbit one dead night\\
Without yet knowing why.

\subsubsection{Verse 2 - Male}\label{verse-2---male}

Lida watches Carlson speak\\
While television glows,\\
He fears each drink will wash away\\
The daughter that he knows.

\subsubsection{Verse 2 - Female}\label{verse-2---female}

Morning breaks through hotel blinds,\\
A Blackberry vibrates,\\
And Müller answers threats with calm\\
While something darker waits.

\subsubsection{Pre-Chorus}\label{pre-chorus-37}

\texttt{{[}Male{]}} One searches for a vanished face,\\
\texttt{{[}Female{]}} One buries what he knows.

\subsubsection{Chorus}\label{chorus-65}

\texttt{{[}Male{]}} Ricochets. \texttt{{[}Female{]}} Ricochets.\\
\texttt{{[}Duet{]}} A bullet strikes a distant wall\\
And still returns somehow.

\texttt{{[}Male{]}} Through Bogotá and New York lights,\\
\texttt{{[}Female{]}} Through bourbon breath and tailored lies,\\
\texttt{{[}Duet{]}} Two strangers orbit one dead night\\
Without yet knowing why.

\subsubsection{Bridge}\label{bridge-16}

\texttt{{[}Male{]}} A boarding house above old streets.\\
\texttt{{[}Female{]}} A luxury hotel beside the park.\\
\texttt{{[}Male{]}} Cheap aspirin dissolving in water.\\
\texttt{{[}Female{]}} French cocktails under painted kings.\\
\texttt{{[}Male{]}} A notebook hidden in a drawer.\\
\texttt{{[}Female{]}} A contract folded in a briefcase.\\
\texttt{{[}Male{]}} Two men waking from different hangovers.\\
\texttt{{[}Female{]}} From Miami neither one fully sober.

\subsubsection{Verse 3 - Male}\label{verse-3---male}

He walks the crowded streets alone,\\
Repeating names like prayers,\\
Afraid that if he stops too long\\
The mission disappears.

\subsubsection{Verse 3 - Female}\label{verse-3---female}

Müller drifts through summer heat\\
With practiced ease and charm,\\
Yet every polished word conceals\\
A quiet state of alarm.

\subsubsection{Pre-Chorus}\label{pre-chorus-38}

\texttt{{[}Male{]}} One fears forgetting why he stayed,\\
\texttt{{[}Female{]}} One fears what stays recalled.

\subsubsection{Chorus}\label{chorus-66}

\texttt{{[}Male{]}} Ricochets. \texttt{{[}Female{]}} Ricochets.\\
\texttt{{[}Duet{]}} A bullet strikes a distant wall\\
And still returns somehow.

\texttt{{[}Male{]}} Through Bogotá and New York lights,\\
\texttt{{[}Female{]}} Through bourbon breath and tailored lies,\\
\texttt{{[}Duet{]}} Two strangers orbit one dead night\\
Without yet knowing why.

\subsubsection{Outro}\label{outro-12}

\texttt{{[}Male{]}} A notebook closes.\\
\texttt{{[}Female{]}} A Blackberry lights again.

\texttt{{[}Male{]}} The city buses keep moving.\\
\texttt{{[}Female{]}} The hotel elevators still rise.

\texttt{{[}Duet{]}}\strut \\
And somewhere between memory and strategy,\\
the first ricochet\\
is already in motion.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{\texorpdfstring{\arabicfont ديانا كاتحمل ثقلها}{Diana Kathmil Tqlha}}

\subsection{Notes}\label{notes-34}

\subsection{Style}\label{style-34}

Contemporary Moroccan pop, Moroccan Darija vocals, 112 BPM, darbouka
groove, bendir accents, syncopated acoustic guitar, oud melodic fills,
fretless bassline, tenor lead vocal, melismatic ornaments, root-note
bass pulse, dry vocal mix, light plate reverb, crisp high-end
transients, wide stereo percussion, bittersweet defiance, forward
momentum

\subsection{Lyrics}\label{lyrics-34}

\subsubsection{Verse 1}\label{verse-1-23}

{\arabicfont بّاها بنى البرج فوق الرمال\\
ف كازا، عند البحر الكبير\\
وشاف بنتو تتعلم الأحوال\\
على طريقة اللي ما كيبانش}

{\arabicfont كانت تقعد هدا الرجال\\
فبرا الباب اللي رسموه\\
وحفظت كيفاش السلطة تمشي\\
قبل ما تمشي، قبل ما تبان}

\subsubsection{Verse 2}\label{verse-2-20}

{\arabicfont باريس عطاتها الـ BBA\\
لندن زادت عليها الـ MBA\\
ومن بعد كوردون بلو ليها وحدها ---\\
داك الشي كان ليها هي}

{\arabicfont مشيتش للشركة، ولا للبّا\\
ولا لما كانو يتوقعو منها ---\\
غير التيراكوتا فم فمها\\
والملح، وما يجيها من قلبها}

\subsubsection{Pre-chorus}\label{pre-chorus-39}

{\arabicfont ولكن ف وسط الحركة\\
بدات تشوف الشكل ---\\
أنو اختيار ما توقفيش\\
هو هربة من نوعو}

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-67}

{\arabicfont كاتحمل جاذبيتها وحدها\\
ما كاين مدار يحبسها طويل\\
عارفة شحال تكلف الوقفة\\
وكاتكمل الطريق}

\subsubsection{Verse 3}\label{verse-3-10}

{\arabicfont ف إيبيثا شافتو كيخدم\\
كل ركن فالقاعة\\
وخلاتو يظن بلي تعارفو ---\\
كانت تستنى هاد اللحظة تلت سنين}

{\arabicfont فالصباح جاء يشوف انستاغرامها\\
وفهم ما كانت عارفاه دايما\\
المسافة بينهوم ضحكتها\\
هي ما كانت ملكو قط}

\subsubsection{Pre-chorus}\label{pre-chorus-40}

{\arabicfont ولكن ف وسط الضحكة\\
بدات تحس بالثقل ---\\
يمكن العمق ما كيحتاجش\\
بلي توقفي باش تلقيه}

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-68}

{\arabicfont كاتحمل جاذبيتها وحدها\\
ما كاين مدار يحبسها طويل\\
عارفة شحال تكلف الوقفة\\
وكاتكمل الطريق}

\subsubsection{Verse 4}\label{verse-4-8}

{\arabicfont كاتعدي من باريس، لندن، تونس\\
فلييت فارغين وليالي مستعارة\\
فنادق المطار مع سوسانة\\
وكل الأضواء الغريبة والمليحة}

{\arabicfont كاتشوف لوسيا كأنها درس ---\\
مرأة حافظت على وزنها\\
ديانا عندها تلاتة وتلاتين\\
وبدات تشوف علاش كانت دايرة دايرة}

\subsubsection{Bridge}\label{bridge-17}

{\arabicfont هي ما عندهاش مشكل مع العمق\\
عندها مشكل مع ثمنو ---\\
الوقوف، الشكل اللي كيتسناو منك\\
النسخة ديالها اللي غادي تخسرها}

{\arabicfont ولكن ``لو'' بدات تحمل أكثر مما تقدر\\
وكاتحس بيه فالغرفة\\
بحال ما حستو ف كازا\\
من سنين، قبل ما يعرف اسمها}

\texttt{{[}Guitar\ riff{]}}

\subsubsection{Chorus}\label{chorus-69}

{\arabicfont كاتحمل جاذبيتها وحدها\\
ما كاين مدار يحبسها طويل\\
عارفة شحال تكلف الوقفة\\
وكاتكمل الطريق}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Espero}\label{espero}

\subsection{Notes}\label{notes-35}

\subsection{Style}\label{style-35}

argentinian zamba, 3/4 pulse, bombo legüero, nylon-string fingerpicking,
bandoneón counterlines, charango tremolo, brushed cajón, male
storytelling vocal, bathroom-room ambience, tile slapback, close mono
mic, tape saturation, bittersweet longing, restrained sorrow, rubato
phrasing, intimate build, plaintive chorus

\subsection{Lyrics}\label{lyrics-35}

Siento que te vayas\\
\strut ~~que tengas que partir en este momento\\
\strut ~~rompiendo el silencio que nos rodea\\
\strut ~~~~en el que nos conocemos\\
\strut ~~~~en el que logramos escuchar nuestras almas

~~Pero ya te has ido\\
\strut ~~~~abandonando impunemente este momento\\
\strut ~~~~quebrando el instante

~~Pero espero\\
\strut ~~~~espero ese nuevo momento de volver a verte\\
\strut ~~~~y seguirte conociendo

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Dapich Sápica}\label{dapich-suxe1pica}

\subsection{Notes}\label{notes-36}

\subsection{Style}\label{style-36}

tango, milonga, dramatic storytelling, 132 BPM, bandoneon stabs,
nylon-string guitar rasgueo, upright bass pizzicato, piano tresillo
figures, violin counterline, male tenor lead, spoken phrasing, theatre
choir, tape saturation, vintage mono horn room, syncopated handclaps,
minor key march, cinematic intro, bittersweet reveal

\subsection{Lyrics}\label{lyrics-36}

Hace dos años que partió el grande,\\
el sabio Dapich, orgullo de Sápica.\\
Los mismos necios que gritaron ``¡que se vaya!''\\
hoy lloran su ausencia con el alma marchita.

Es invierno feroz, la nieve castiga,\\
los pinos se doblan bajo el peso del hielo.\\
El viento aúlla como un lobo en la cima\\
y el frío muerde más hondo que un acero.

Los hombres, con manos agrietadas y duras,\\
subidos a techos que crujen de pena,\\
clavan y remiendan con furia y premura\\
mientras el cielo amenaza tormenta.

Y en medio del blanco, un niño inocente,\\
jugando con nieve que tiñe de frío,\\
ve una figura que avanza lentamente---\\
negra contra el blanco, como un mal augurio.

Los viejos de Sápica ya saben quién viene,\\
las mujeres se asoman con ojos cansados.\\
Todos lo saben\ldots{} pero nadie lo dice,\\
porque duele el regreso del que nada ha hallado.

Camina vencido, el poncho hecho harapos,\\
espaldas cargadas con toda la ausencia.\\
El niño lo mira, le tiembla la mano\ldots{}\\
y aún así le sonríe con ternura inmensa.

Pasa a su lado, lento, sin palabras.\\
El viento se calla, parece que espera.\\
Y ahí, frente a toda la aldea callada,\\
cae la verdad como un puñal en la niebla---

No era el sabio.

Era su hijo.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Gota a gota}\label{gota-a-gota}

\subsection{Notes}\label{notes-37}

\subsection{Style}\label{style-37}

delicate female lead, goth metal, dubstep with heavy distortions

\subsection{Lyrics}\label{lyrics-37}

~~Crash! Pum! Cataplún! Zap!

~~~~Plif! Chap! Punch! Prak!

~~~~~~Paff! Zambomba! Krak! Zzip!

~---

¡plic! ¡ploc! Gota a gota caía la lluvia.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Cataplún Zap!}\label{catapluxfan-zap}

\subsection{Notes}\label{notes-38}

\subsection{Style}\label{style-38}

dubstep, 140 BPM, half-time groove, syncopated sub drops, delicate
female soprano, chopped vocal syllables, staccato percussion vocals,
metallic found sounds, punchy snare hits, distorted reese bass, wobble
bass flourishes, sidechain pumping, dark plate reverb, wide stereo
imaging, analog saturation, glitch edits, cinematic intro, tense release

\subsection{Lyrics}\label{lyrics-38}

~~Crash! Pum! Cataplún! Zap!

~~~~Plif! Chap! Punch! Prak!

~~~~~~Paff! Zambomba! Krak! Zzip!

~---

¡plic! ¡ploc! Gota a gota caía la lluvia.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Street Corner Zambomba}\label{street-corner-zambomba}

\subsection{Notes}\label{notes-39}

\subsection{Style}\label{style-39}

Electroswing with a high-tempo dance beat at 124 BPM in F minor. The
track features a prominent brass section with trumpets and trombones
playing syncopated staccato stabs. A synthesized upright bass provides a
walking bassline that interacts with a four-on-the-floor kick drum and a
crisp, high-frequency snare. A bright, processed female vocal performs
repetitive melodic hooks with heavy compression and a slight slapback
delay. Glitchy record scratches and vinyl crackle effects are layered
over the percussion. A swing-style piano plays rhythmic chords on the
off-beats. The arrangement uses sudden filter sweeps and momentary
silences for rhythmic emphasis.

\subsection{Lyrics}\label{lyrics-39}

\subsubsection{Intro}\label{intro-14}

\texttt{{[}four-on-the-floor\ kick\ drum,\ vinyl\ crackle,\ staccato\ brass\ stabs{]}}\strut \\
Crash! Pum! Cataplún! Zap!\\
\texttt{{[}record\ scratch{]}}\strut \\
Plif! Chap! Punch! Prak!\\
\texttt{{[}full\ band\ enters,\ walking\ synth\ bass,\ swing\ piano{]}}\strut \\
Paff! Zambomba! Krak! Zzip!

\subsubsection{Chorus}\label{chorus-70}

\texttt{{[}processed\ female\ vocals,\ bright\ brass\ section{]}}\strut \\
¡plic! ¡ploc! Gota a gota caía la lluvia.

\subsubsection{Outro}\label{outro-13}

\texttt{{[}filter\ sweep\ on\ brass{]}}\strut \\
Y volvió\ldots{} lloviendo en todas partes y escampando en tu mirada

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Gabi's Shoulder}\label{gabis-shoulder}

\subsection{Notes}\label{notes-40}

\subsection{Style}\label{style-40}

blues rock, electro blues, 117 BPM, baritone lead, close mic vocals,
intimate delivery, overdriven electric guitar, tremolo guitar swells,
fretless bass slides, brushed snare kit, halftime dubstep bridge,
sub-bass drop, analog synth pads, spring reverb, tape saturation, swung
backbeat, off-kilter phrasing, bittersweet intimacy, nocturnal cityscape

\subsection{Lyrics}\label{lyrics-40}

\subsubsection{Verse 1}\label{verse-1-24}

The show closed quiet, not quite the win they'd planned,\\
Mariain caught it in Gabi's eyes before the car stopped.\\
No words in the back of a stranger's machine,\\
just her shoulder finding Gabi's in the dark.\\
The Upper East Side waiting, soft and indifferent,\\
the week dissolving somewhere on the bridge.

\subsubsection{Verse 2}\label{verse-2-21}

Elevator slow, they leaned without speaking,\\
fatigue like a second coat, heavy and thin.\\
Sylvia glowing at the door, already reading the room,\\
Thomas somewhere in the library blue ---\\
the penthouse swallowed them in,\\
low lights, familiar air, Manhattan spread below.

\subsubsection{Pre-Chorus}\label{pre-chorus-41}

She always knows before it's said,\\
reads the weather in a glance ---\\
the soft machinery running quiet\\
underneath the circumstance.

\subsubsection{Chorus}\label{chorus-71}

The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
this is how they live,\\
this is what they give.

\subsubsection{Verse 3}\label{verse-3-11}

Gabi found him at the desk, wrapped her arms around him,\\
kissed his neck and breathed him in ---\\
it wasn't great, but it was ours.\\
Low music, easy talk, the four of them loose,\\
drinks and small plates and the city below,\\
nobody performing, nobody keeping score.

\subsubsection{Pre-Chorus}\label{pre-chorus-42}

She kissed Gabi at the door,\\
then turned and kissed Thomas too ---\\
unhurried, warm, the way you kiss\\
what you already know is true.\\
Then out into the Village night,\\
the one who always walks back alone.

\subsubsection{Chorus}\label{chorus-72}

The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
this is how they live,\\
this is what they give.

\subsubsection{Bridge}\label{bridge-18}

Morning came with bacon\\
and Sylvia's gentle knock ---\\
Gabi groaned into the pillows,\\
hair wild from the clock.\\
Cab to Mariain's,\\
a text: might miss you ---\\
the bag already packed,\\
the room already knew.\\
Outside the gallery,\\
thirty seconds, arms and fabric ---\\
safe flight ---\\
I'll message when we land ---\\
then taillights into the afternoon,\\
six hours of southern sky,\\
Bogotá lights like broken glass\\
scattered on the plateau ground,\\
Alicia rushing up the stairs,\\
arms open, spinning round.

\subsubsection{Verse 4}\label{verse-4-9}

SUV climbing through the thin cool air,\\
gummies and New York sweets passed around.\\
Dropped Alicia at her mother's, waited till she was in,\\
then three more blocks to home.\\
Gabi turned the lights on, checked the rooms,\\
Sylvia claimed his left shoulder,\\
Gabi settled on his right ---\\
Thomas wrapped an arm around each,\\
the fireplace low,\\
the city quiet on the other side of the glass.

\subsubsection{Pre-Chorus}\label{pre-chorus-43}

No grand declarations,\\
just the weight of arms and breathing slow ---\\
the soft machinery of love\\
that only insiders know.

\subsubsection{Chorus - Outro}\label{chorus---outro}

The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
exhibitions come and go,\\
but this is what survives.\\
The unspoken rhythm,\\
low and sure,\\
the particular light,\\
the particular door ---\\
Mariain walking back through the Village,\\
Gabi on his shoulder,\\
the city holding all of it,\\
the way it always has.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Unspoken Rhythm}\label{unspoken-rhythm}

\subsection{Notes}\label{notes-41}

\subsection{Style}\label{style-41}

new age techno, cinematic dubstep, 132 BPM, female soprano lead, male
baritone rap, distorted vocal chops, sub-bass drops, sidechained synth
pads, metallic percussion, tabla pulses, glassy arps, bathroom room
tone, tiled slapback, syncopated half-time, staggered breaks,
call-and-response chorus, melancholic intimacy, dramatic build,
Latin-Mediterranean hooks

\subsection{Lyrics}\label{lyrics-41}

\subsubsection{Chorus}\label{chorus-73}

\texttt{{[}Melodic,\ female\ soprano\ vocals{]}}\strut \\
The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
this is how they live,\\
this is what they give.

\subsubsection{Chorus}\label{chorus-74}

\texttt{{[}Melodic,\ female\ soprano\ vocals{]}}\strut \\
The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
this is how they live,\\
this is what they give.

\subsubsection{Bridge}\label{bridge-19}

\texttt{{[}Rap,\ male\ baritone\ vocals{]}}\strut \\
Morning came with bacon\\
and Sylvia's gentle knock ---\\
Gabi groaned into the pillows,\\
hair wild from the clock.\\
Cab to Mariain's,\\
a text: might miss you ---\\
the bag already packed,\\
the room already knew.\\
Outside the gallery,\\
thirty seconds, arms and fabric ---\\
safe flight ---\\
I'll message when we land ---\\
then taillights into the afternoon,\\
six hours of southern sky,\\
Bogotá lights like broken glass\\
scattered on the plateau ground,\\
Alicia rushing up the stairs,\\
arms open, spinning round.

\subsubsection{Chorus - Outro}\label{chorus---outro-1}

\texttt{{[}Melodic,\ female\ soprano\ vocals{]}}\strut \\
The unspoken rhythm,\\
no map, no name,\\
just the way they move together\\
through the ordinary strange.\\
The unspoken rhythm ---\\
exhibitions come and go,\\
but this is what survives.\\
The unspoken rhythm,\\
low and sure,\\
the particular light,\\
the particular door ---\\
Mariain walking back through the Village,\\
Gabi on his shoulder,\\
the city holding all of it,\\
the way it always has.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{The Night}\label{the-night}

\subsection{Notes}\label{notes-42}

\subsection{Style}\label{style-42}

Contemporary Arabic Pop featuring a male tenor lead vocal. The
arrangement is centered around a bright, strummed acoustic guitar and a
prominent fretless bass that performs melodic slides and syncopated
fills. A traditional Arabic percussion ensemble provides the rhythmic
drive, featuring the sharp, metallic snap of a darbuka and the deep
resonance of a riq. The tempo is 105 BPM in 4/4 time, set in the key of
D Major. The vocal delivery is characterized by melismatic ornamentation
and moderate plate reverb. A clean electric guitar provides subtle
melodic counterpoint in the higher register during vocal pauses. The mix
is clean with a wide stereo image for the percussion and a centered, dry
vocal presence.

\subsection{Lyrics}\label{lyrics-42}

\subsubsection{Intro}\label{intro-15}

\texttt{{[}strummed\ acoustic\ guitar,\ fretless\ bass\ slides,\ darbuka\ and\ riq\ percussion{]}}

\subsubsection{Verse 1}\label{verse-1-25}

\texttt{{[}male\ tenor\ vocals\ with\ melismatic\ ornamentation{]}}\strut \\
The night extends without an end,\\
A sleepless dream I cannot leave,\\
Where all remembered shadows bend\\
Through what remains of self-belief.\\
The hours gather, dark and slow,\\
Like voices pressing through a wall,\\
And every thought I used to know\\
Returns the moment nightfall calls.\\
The mind becomes a narrow room\\
Where memory learns at last to bloom.

\texttt{{[}Instrumental\ Break{]}}

\subsubsection{Chorus}\label{chorus-75}

The night returns with silent weight,\\
And memory crowds the dark again,\\
While sleepless hours accumulate\\
Like slowly falling winter rain.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Strangers in the Light}\label{strangers-in-the-light}

\subsection{Notes}\label{notes-43}

\subsection{Style}\label{style-43}

pop ballad, 126 BPM, mezzo vocals, close-mic intimacy, grand piano
arpeggios, legato string quartet, electric guitar swells, fretless bass,
brushed snare groove, syncopated hand percussion, sidechain pumping,
plate reverb, tape saturation, café ambience, bittersweet intimacy,
morning light, chorus lift, spoken pre-chorus

\subsection{Lyrics}\label{lyrics-43}

\subsubsection{Verse 1}\label{verse-1-26}

In a busy café's glow, Brittany sat alone\\
Sipping coffee, heart at peace, lost in thoughts her own\\
A quiet strength wrapped round her like the morning sun\\
She felt the world fade gently, her calm had just begun

\subsubsection{Verse 2}\label{verse-2-22}

Across the room sat Thomas, shy glances filled with care\\
A quiet longing stirred in him, yet timid was his stare\\
His settled life felt heavy, but something new took flight\\
When her eyes met his softly in the golden morning light

\subsubsection{Pre-Chorus}\label{pre-chorus-44}

Something whispered in the silence, pulling two hearts near\\
Nerves and courage danced together, overcoming fear

\subsubsection{Chorus}\label{chorus-76}

Two strangers found connection in the moment they were true\\
Baring scars and hidden stories, making something new\\
Through the walls we build so tightly, vulnerability's key\\
In each other's honest eyes, two lonely souls felt free

\subsubsection{Verse 3}\label{verse-3-12}

She crossed the space with courage, soft words broke through the air\\
He welcomed her with wonder, surprised but glad she dared\\
Their laughter flowed like river, then deeper talks arose\\
Of broken pasts and quiet hopes that only few disclose

\subsubsection{Pre-Chorus}\label{pre-chorus-45}

In her small and flowery room, layers fell away\\
Hearts laid open, fears were spoken in the soft lamp's ray

\subsubsection{Chorus}\label{chorus-77}

Two strangers found connection in the moment they were true\\
Baring scars and hidden stories, making something new\\
Through the walls we build so tightly, vulnerability's key\\
In each other's honest eyes, two lonely souls felt free

\subsubsection{Bridge}\label{bridge-20}

She spoke of youthful marriage lost and pain she overcame\\
He shared a faded union and the children that he named\\
No easy roads before them, yet comfort filled the space\\
Two wounded hearts found healing in that tender, brief embrace

\subsubsection{Verse 4}\label{verse-4-10}

They traded numbers, longing, as the daylight said goodbye\\
``I miss you already,'' came her message by and by\\
On the metro back to solitude, he smiled through the ache\\
A spark of hope now burning for love's unexpected sake

\subsubsection{Pre-Chorus}\label{pre-chorus-46}

Though tomorrow brings uncertainty and miles stretch between

\subsubsection{Chorus - Outro}\label{chorus---outro-2}

\texttt{{[}Fading\ instrumentation{]}}\strut \\
Two strangers found connection in the moment they were true\\
Baring scars and hidden stories, making something new\\
Through the walls we build so tightly, vulnerability's key\\
In each other's honest eyes\ldots{} our lonely souls are free

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Café Glance}\label{cafuxe9-glance}

\subsection{Notes}\label{notes-44}

\subsection{Style}\label{style-44}

pop ballad, cinematic dubstep, 143 BPM, mezzo vocals, layered synth
pads, arpeggiated synth plucks, sub-bass drop, gated snare build,
sidechain pumping, plate reverb, stereo delay throws, half-time
breakdown, verse pre-chorus lift, anthem chorus, bittersweet romance,
sunlight imagery

\subsection{Lyrics}\label{lyrics-44}

\subsubsection{Verse 1}\label{verse-1-27}

Morning light spilled golden through the bustling café glass\\
Brittany sat so graceful at her tall and slender glass\\
Flowery sundress dancing green and yellow on her frame\\
Cartwheel hat sat tilted, like a flower in full flame

\subsubsection{Versr 2}\label{versr-2}

Thomas watched from shadows in his corner tucked away\\
Purple polo snug and neat, blue jeans worn from every day\\
His dark eyes kept returning, stealing glares he couldn't hide\\
Heartbeats quickened softly in the swirl of steam and tide

\subsubsection{Pre-Chorus}\label{pre-chorus-47}

Tension hummed between them like the clatter of the cups\\
Shyness held him frozen while her courage started up

\subsubsection{Chorus}\label{chorus-78}

Cartwheel hat and sundress, spinning colors in the air\\
Purple polo, faded jeans, caught in a silent stare\\
Glares turned into courage, shyness met with bold initiative\\
Two hearts dressed in sunlight found a spark so delicate

\subsubsection{Verse 3}\label{verse-3-13}

She rose with flowing movement, dress swaying as she walked\\
Hat brim casting playful shade where confidence now talked\\
He straightened in his polo, cheeks warm with shy surprise\\
Her smile cut through his quiet like sunlight in his eyes

\subsubsection{Pre-Chorus}\label{pre-chorus-48}

Words began to tumble soft, the world around grew dim\\
Visuals turned to feeling in the glow that shone on them

\subsubsection{Chorus}\label{chorus-79}

Cartwheel hat and sundress, spinning colors in the air\\
Purple polo, faded jeans, caught in a silent stare\\
Glares turned into courage, shyness met with bold initiative\\
Two hearts dressed in sunlight found a spark so delicate

\subsubsection{Bridge}\label{bridge-21}

Freckles on her shoulders, gray strands in his beard\\
Vitiligo patterns, stories that the eyes revered\\
In that crowded café, simple clothes and quiet gaze\\
Painted beauty in the ordinary passing days

\subsubsection{Verse 4}\label{verse-4-11}

They stepped out hand in hand, her hat against the breeze\\
His polo slightly wrinkled from the warmth of new release\\
Café visuals lingered like a picture in their minds\\
A fleeting frame of color where two lonely paths aligned

\subsubsection{Pre-Chorus}\label{pre-chorus-49}

Though the moment fades to memory, the image still remains

\subsubsection{Chorus - Outro}\label{chorus---outro-3}

Cartwheel hat and sundress, spinning colors in the air\\
Purple polo, faded jeans, caught in a silent stare\\
Glares turned into courage, shyness met with bold initiative\\
Two hearts dressed in sunlight\ldots{} found a spark so delicate

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Petals and Ink}\label{petals-and-ink}

\subsection{Notes}\label{notes-45}

\subsection{Style}\label{style-45}

country pop ballad, theatrical pop, 132 BPM, mezzo belting vocals,
acoustic guitar strums, piano arpeggios, brushed snare, hand percussion,
upright bass, pedal steel swells, mandolin accents, warm plate reverb,
chorus lifted hook, swung eighth feel, bittersweet vulnerability,
intimate reveal

\subsection{Lyrics}\label{lyrics-45}

\subsubsection{Verse 1}\label{verse-1-28}

In her flowery sundress, green and yellow soft and bright\\
Cartwheel hat still tilted, catching fragments of the light\\
She stood before him trembling, letting fabric slowly fall\\
Revealing every secret that her skin and spirit called

\subsubsection{verse 2}\label{verse-2-23}

``Habibi'' traced in Arabic across her left clavicle\\
Blue butterfly on neckline, wings of fragile miracle\\
Rose upon her lower back, tribal patterns wrapped around\\
Om sign on her ankle, where her spirit touched the ground

\subsubsection{Pre-Chorus}\label{pre-chorus-50}

In the soft glow of her room, she opened up so wide\\
Every mark and every story, nothing left to hide

\subsubsection{Chorusl}\label{chorusl}

Flowery dress and cartwheel hat, now scattered on the floor\\
Tattoos and piercings telling what her heart had worn\\
In her sanctuary she stood, vulnerable and true\\
Letting Thomas see the colors only she once knew

\subsubsection{Verse 3}\label{verse-3-14}

Pink duvet on wooden bed, white pillows crisp and clean\\
Cottage lamp cast gentle gold on all her quiet dreams\\
Self-help books and trinkets on the dressing table small\\
Venetian blinds half open, letting twilight gently fall

\subsubsection{Pre-Chorus}\label{pre-chorus-51}

She shared her broken marriages, the pain, the strength, the scars\\
While he drank in her presence beneath the bedroom stars

\subsubsection{Chorus}\label{chorus-80}

Flowery dress and cartwheel hat, now scattered on the floor\\
Tattoos and piercings telling what her heart had worn\\
In her sanctuary she stood, vulnerable and true\\
Letting Thomas see the colors only she once knew

\subsubsection{Bridge}\label{bridge-22}

\texttt{{[}Whispered,\ almost\ spoken{]}}\strut \\
Cross pendant gently swaying, silver rings upon her ears\\
She whispered she was ready to release her hidden fears\\
Her small room held her safely, every corner spoke her name\\
A fragile, flowery haven where she no longer felt ashamed

\subsubsection{Verse 4}\label{verse-4-12}

As layers dropped and stories flowed, her eyes met his with trust\\
The wardrobe full of memories, the chair where she'd adjust\\
In this tender revelation, clothed only in her truth\\
She bloomed before his gentle gaze, reborn in quiet youth

\subsubsection{Pre-Chorus}\label{pre-chorus-52}

Her decorated haven witnessed hearts beginning to entwine

\subsubsection{Chorus - Outro}\label{chorus---outro-4}

Flowery dress and cartwheel hat, now scattered on the floor\\
Tattoos and piercings telling what her heart had worn\\
In her sanctuary she stood, vulnerable and true\\
Letting Thomas see the beauty\ldots{} only she once knew

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Balance of Three}\label{balance-of-three}

\subsection{Notes}\label{notes-46}

\subsection{Style}\label{style-46}

glam metal, 136 BPM, C G Am F progression, close-mic baritone vocals,
grand piano stabs, baritone sax riffs, acoustic guitar strums, tambora
accents, string swells, distorted electric lead, gang vocal chorus, tape
saturation, spring reverb, gated snare, minor key menace

\subsection{Lyrics}\label{lyrics-46}

\subsubsection{Verse 1}\label{verse-1-29}

We build our lives on shifting ground\\
Where order keeps the world around\\
Yet freedom calls, a voice so clear\\
And equity draws all near

\subsubsection{Pre-Chorus}\label{pre-chorus-53}

Three forces pull, they intertwine\\
A dance of hearts, a grand design\\
We choose our path, we take our stand\\
The wheel turns on across the land

\subsubsection{Chorus}\label{chorus-81}

Balance of three, the world we see\\
Order, freedom, equity\\
Spin the wheel, let voices rise\\
Together we can harmonize

\subsubsection{Verse 2}\label{verse-2-24}

The conservative holds the frame\\
The libertarian lights the flame\\
The socialist seeks equal share\\
Each vision shapes the world we bear

\subsubsection{Pre-Chorus}\label{pre-chorus-54}

Extremes may break, but still we try\\
To find the truth where futures lie\\
The wheel of thought, it spins anew\\
And every choice belongs to you

\subsubsection{Chorus}\label{chorus-82}

Balance of three, the world we see\\
Order, freedom, equity\\
Spin the wheel, let voices rise\\
Together we can harmonize

\subsubsection{Bridge}\label{bridge-23}

Fascist walls, anarchist cries\\
Communist dreams, collectivist ties\\
But in the center, hope remains\\
A song of balance breaks the chains

\subsubsection{Final Chorus}\label{final-chorus-5}

Balance of three, the world we see\\
Order, freedom, equity\\
Spin the wheel, let voices rise\\
Together we can harmonize

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Royal Docks}\label{royal-docks}

\subsection{Notes}\label{notes-47}

\subsection{Style}\label{style-47}

house, club dubstep, 132 BPM, female belt vocals, received
pronunciation, punchy kick drum, syncopated house bass, sidechained
synth bass, metallic percussion, filtered trance pads, gated snare, wide
stereo claps, plate reverb, tape saturation, half-time bridge,
spoken-sung delivery, anthemic release, late-night isolation

\subsection{Lyrics}\label{lyrics-47}

\subsubsection{\texorpdfstring{Verse 1 --- \emph{Cardiff, the
leaving}}{Verse 1 --- Cardiff, the leaving}}\label{verse-1-cardiff-the-leaving}

\texttt{{[}female\ vocals,\ house\ beat,\ soothing{]}}\strut \\
She loved the city that she left behind\\
The bay, the castle, the rain-grey light\\
But memory cuts like a Cardiff knife\\
So she packed her bags on a Tuesday night

Ex at the door and the family gone cold\\
Twenty-six and already too old\\
For a place that knew her before she knew\\
What she was going to become

\subsubsection{\texorpdfstring{Verse 2 --- \emph{London arrival, the
flat, the friends too
spread}}{Verse 2 --- London arrival, the flat, the friends too spread}}\label{verse-2-london-arrival-the-flat-the-friends-too-spread}

\texttt{{[}female\ vocals,\ house\ beat,\ soothing{]}}\strut \\
First it was Barking, a house share and rain\\
Four girls and a kitchen and the Overground strain\\
LCY mornings before anyone's up\\
Charter runs, regional work, keep the head down

Then Thomas, Rotterdam, the role that grew\\
Royal Docks flat when the money came through\\
Her name on a lease that she signed on her own\\
The first proper place she could call her own

In a street where everyone knew your name

\subsubsection{Pre-Chorus}\label{pre-chorus-55}

\texttt{{[}female\ vocals,\ dubstep\ drop,\ soothing,\ restrained{]}}\strut \\
Her stuff is there\\
The shelf, the coat\\
The mug she bought\\
Because she thought\\
She'd stay

\subsubsection{Chorus}\label{chorus-83}

\texttt{{[}female\ vocals,\ peak\ energy,\ \ repetitive\ hook{]}}\strut \\
(Royal Docks, fourth floor)\\
Her name's on the door\\
But the flat doesn't know her\\
Like she knows the air\\
Her stuff on the shelves\\
(But she's never quite there)

(Royal Docks, fourth floor)\\
The address that holds her\\
When nothing else does\\
(When nothing else does)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{\texorpdfstring{Verse 3 --- \emph{Thomas in London, the
PCL flat, the role that
shifts}}{Verse 3 --- Thomas in London, the PCL flat, the role that shifts}}\label{verse-3-thomas-in-london-the-pcl-flat-the-role-that-shifts}

\texttt{{[}female\ vocals,\ house\ beat,\ soothing{]}}\strut \\
He calls it business when he's in town\\
Advisor and aide when the others are round\\
But Pilar's downstairs and Gabi's away\\
And London goes quiet at the end of the day

PCL flat and a different register\\
She's not the crew chief and he's not the principal\\
Just two people in a city at night\\
Which is something she keeps very close to the light

\subsubsection{Pre-Chorus}\label{pre-chorus-56}

\texttt{{[}female\ vocals,\ dubstep\ drop,\ soothing,\ restrained{]}}\strut \\
Her stuff is there\\
The shelf, the coat\\
The mug she bought\\
Because she thought\\
She'd stay

\subsubsection{Chorus}\label{chorus-84}

\texttt{{[}female\ vocals,\ peak\ energy,\ \ repetitive\ hook{]}}\strut \\
(Royal Docks, fourth floor)\\
Her name's on the door\\
But the flat doesn't know her\\
Like she knows the air\\
Her stuff on the shelves\\
(But she's never quite there)

\subsubsection{Bridge}\label{bridge-24}

\texttt{{[}female\ vocals,\ half-time\ feel,\ stripped\ back,\ spoken-sung{]}}\strut \\
Diana rings when she's passing through\\
(Come out, come out, the city's for you)\\
Fiona texts from a pub somewhere east\\
Vicky's free if Erika's in from Utrecht this week

They pull her out of the Royal Docks quiet\\
Into the city she still hasn't claimed\\
And for three hours London almost fits\\
Before she's back at the door again

\subsubsection{\texorpdfstring{Verse 4 --- \emph{the orbit as the real
geography}}{Verse 4 --- the orbit as the real geography}}\label{verse-4-the-orbit-as-the-real-geography}

\texttt{{[}female\ vocals,\ house\ beat,\ soothing{]}}\strut \\
She's got Barcelona logged in her bones\\
And the Embraer routing she could fly alone\\
The Rotterdam handlers know her name\\
The PCL concierge does the same

Every city holds a version of her\\
Warmer and sharper than the zone-two flat\\
But the lease renews and the address stays\\
Because a woman like Claire needs somewhere to land

\subsubsection{Pre-Chorus}\label{pre-chorus-57}

\texttt{{[}female\ vocals,\ slightly\ elongated,\ dubstep\ drop,\ soothing{]}}\strut \\
Her stuff is there\\
The shelf, the coat\\
The mug she bought\\
Because she thought ---\\
She'd stay\\
She always thought\\
She'd stay

\subsubsection{Chorus}\label{chorus-85}

\texttt{{[}female\ vocals,\ fool\ energy,\ \ layered{]}}\strut \\
(Royal Docks, fourth floor)\\
Her name's on the door\\
But the flat doesn't know her\\
Like she knows the air\\
(Diana says come out)

Her stuff on the shelves\\
But she's never quite there\\
(Fiona's got a table)

Royal Docks, fourth floor\\
(Vicky's in from Bethnal Green)

The address that holds her\\
When nothing else does\\
(PCL at midnight)

When nothing else does\\
(still the best thing she's got)

When nothing else does

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Berent Steel (Opa's Shadow)}\label{berent-steel-opas-shadow}

\subsection{Notes}\label{notes-48}

\subsection{Style}\label{style-48}

glam metal, 148 BPM, power ballad lift, baritone lead vocals, female
harmony stack, dual language phrasing, twin electric guitars, palm-muted
riffs, shred guitar fills, melodic basslines, arena drums, gated snare
reverb, plate reverb, tape saturation, stereo delay throws, dramatic
pre-chorus build, anthemic resolve, caught urgency

\subsection{Lyrics}\label{lyrics-48}

\subsubsection{Intro}\label{intro-16}

\texttt{{[}Heavy\ riff,\ spoken{]}}\strut \\
Kościerzyna\ldots{} Berent\ldots{} Opa\ldots{}

\subsubsection{Verse 1}\label{verse-1-30}

Dans les rues de cette petite ville polonaise\\
Pierre tombale grise, Müller gravé en lettres fanées\\
Je cherche mon sang, mais ce nom est trop commun\\
Opa fuyait la guerre, Danzig, Königsberg, puis Colombie à dix-huit ans

Empire allemand, puis Pologne en vingt\\
Les nazis sont revenus, tout a brûlé encore\\
Maintenant c'est polonais, l'âme allemande effacée

\subsubsection{Pre-Chorus}\label{pre-chorus-58}

Sophie me regarde, bière à la main, sourire en coin\\
« Pourquoi on traîne ici, Fabián ? »\\
Je lui réponds en riant : « Pour pas voir ta mère, baby ! »

\subsubsection{Chorus}\label{chorus-86}

\textbf{Berent Steel!} Opa's calling me!\\
\textbf{Heimat verloren}, but the blood still screams!\\
Qu'est-ce que vaut l'héritage ? Fire in the veins!\\
Glam in the ruins, we're breaking these chains!\\
\textbf{Yeah!} Lost roots, wild hearts, never tame!\\
\textbf{Berent Steel!} Forever in flame!

\subsubsection{Verse 2}\label{verse-2-25}

Elle me parle de son grand-père français mort en Côte d'Ivoire\\
Des cousins lointains qu'elle n'a jamais voulu voir\\
Moi je cherche mes grands-oncles, peut-être ils ont porté l'aigle noir\\
Opa haïssait les deux côtés --- Nazis et Soviets, fuck them all!

« Tu fais l'imbécile encore, Fabián ! »\\
Ouais, mais il est temps d'être l'imbécile du système, darling\\
Los Angeles attend, Mr.~Michel va crier\\
Mais ce soir on boit\ldots{}

\subsubsection{Chorus}\label{chorus-87}

\textbf{Berent Steel!} Opa's calling me!\\
\textbf{Heimat verloren}, but the blood still screams!\\
Qu'est-ce que vaut l'héritage ? Fire in the veins!\\
Glam in the ruins, we're breaking these chains!\\
\textbf{Yeah!} Lost roots, wild hearts, never tame!\\
\textbf{Berent Steel!} Forever in flame!

\subsubsection{Bridge}\label{bridge-25}

\texttt{{[}Half-time,\ emotional{]}}\strut \\
Sous les étoiles polonaises, deux âmes un peu cassées\\
German ghost in my blood, Colombian fire in me\\
French blood in hers, distant and free\\
Peut-être que l'héritage c'est juste ça\ldots{}\\
Vivre plus fort que ceux qui ont tout effacé!

\texttt{{[}Explosive\ guitar\ solo{]}}

\texttt{{[}Final\ Chorus\ /\ Outro{]}}\strut \\
\textbf{Berent Steel!} Opa's calling me!\\
Sophie tend sa bière, elle crie dans la nuit :\\
\textbf{« Aux grands-oncles qui ne nous ont jamais mérités ! »}

\textbf{Mein Blut, ton âme}, wild and free!\\
Qu'est-ce que vaut l'héritage ?\\
\textbf{C'est nous qui décidons, baby!}

\textbf{Berent Steel!}\\
\textbf{Kościerzyna nights} --- we own this memory!\\
\textbf{Yeah! Yeah!} Forever in flame!

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{Chiang Mai to Bangkok}\label{chiang-mai-to-bangkok}

\subsection{Notes}\label{notes-49}

\subsection{Style}\label{style-49}

K-pop dance-pop with bright syncopated drums, glossy synth plucks,
bouncing bass, and a four-on-the-floor lift in the chorus; verses stay
percussive with clipped lead vocals and playful chant replies,
pre-chorus opens with stacked harmonies and a rising filter sweep,
chorus bursts into group hooks and handclaps. Whispered ad-libs,
pitch-shifted photo-flash chops, reverse swell transitions, crisp and
neon-bright mix., k-pop, warm, world

\subsection{Lyrics}\label{lyrics-49}

\subsubsection{Verse 1}\label{verse-1-31}

Thailand in my carry-on\\
Ugenito went sideways, I kept on\\
Chiang Mai lights, Bangkok heat\\
Every bad plan learned to dance on its feet

Photos turn to little scenes\\
Albums fold up bigger meanings\\
I see the map, then I see me\\
One bad joke and a system key

\subsubsection{Pre-Chorus}\label{pre-chorus-59}

Claim and crack\\
Mask and fact\\
We point at the mess\\
Then trace it back

Wrong advice\\
Right in sight\\
Tune it up\\
Don't set it tight

\subsubsection{Chorus}\label{chorus-88}

Chiang Mai to Bangkok\\
(Chiang Mai to Bangkok)\\
I keep connecting dots\\
I keep connecting dots

From Florida sand to airport lines\\
From family noise to changing signs\\
I keep connecting dots\\
I keep connecting dots

\subsubsection{Verse 2}\label{verse-2-26}

IMO in the Chiang Mai room\\
Filing the world in a small hotel gloom\\
Transit rules and temple bells\\
Popular faith and the stories it tells

Curfew became the task\\
A joke that turned into a mask\\
Overthinker, underachiever, same\\
Trying to grow up without a game

\subsubsection{Pre-Chorus}\label{pre-chorus-60}

Claim and crack\\
Mask and fact\\
We point at the mess\\
Then trace it back

Wrong advice\\
Right in sight\\
Tune it up\\
Don't set it tight

\subsubsection{Chorus}\label{chorus-89}

Chiang Mai to Bangkok\\
(Chiang Mai to Bangkok)\\
I keep connecting dots\\
I keep connecting dots

From Florida sand to airport lines\\
From family noise to changing signs\\
I keep connecting dots\\
I keep connecting dots

\subsubsection{Bridge}\label{bridge-26}

Thomas cut warm at landing\\
Before the talk, before the standing\\
Gabi saw it clear\\
No need to force the fear

Sylvia says, ``I'm not in love''\\
But Gabi reads what's up above\\
Not the line, but what it hides\\
The old self living in the eyes

\subsubsection{Final Chorus}\label{final-chorus-6}

Chiang Mai to Bangkok\\
(Chiang Mai to Bangkok)\\
I keep connecting dots\\
I keep connecting dots

From Thomas to the turning tide\\
From late two-zero to mid two-one wide\\
I keep connecting dots\\
I keep connecting dots

(Connecting dots)\\
(Connecting dots)

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\section{{[}title{]}}\label{title}

\subsection{Notes}\label{notes-50}

\subsection{Style}\label{style-50}

\subsection{Lyrics}\label{lyrics-50}

\end{document}
